---
title             : "Measuring Adults' and Children's Comprehension of Disjunction"
shorttitle        : "Measuring Comprehension of Disjunction"
author: 
  - name          : "Masoud Jasbi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Boylston Hall, Cambridge, MA"
    email         : "masoud_jasbi@fas.harvard.edu"
  - name          : "Michael C. Frank"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Harvard University"
  - id            : "2"
    institution   : "Stanford University"

author_note: |
  All the experimental materials, data, randomization code, and analysis code for the studies reported in this paper are available in the following online repository: [https://github.com/jasbi/disjunction_comprehension](https://github.com/jasbi/disjunction_comprehension). The repository also includes instructions for reproducing this research.

abstract: |
  Disjunction has been a central topic in the literature on children's semantic development. Previous research suggests that adults and children might differ in their interpretation of linguistic disjunction in two ways. First, unlike adults, children might interpret a disjunction as conjunction [@Singh2016; @tieu2016]. Second, children might interpret *or* as inclusive disjunction when adults interpret it as exclusive [@crain2012emergence]. We first review the long tradition of research on children's development of disjunciton. We argue that previous research suggests conjunctive readings of disjunction are mainly due to task demands. Then we present three studies that assess adults and children's understanding of *and* and *or* using three different measures: binary truth value judgments, ternary truth value judgments, and free-form verbal feedback. We report that children and adults do not differ in their binary judgments of disjunction. With ternary judgments, they show similar results except when both disjuncts are true. Adults tend to rate such disjunctions lower (exclusivity implicatures) while children consider them "right". In their free-form verbal feedback, however, children explicitly correct such infelicitous disjunctions and suggest that the connective *and* should have been used instead of *or*. These results suggest that forced-choice truth-value judgments may underestimate children's pragmatic competence. In order to capture children's semantic as well as pragmatic competence, we recommend complementing truth value judgment tasks with measures more sensitive to pragmatic infelicities.
  
  Issues of measurement. Implications for pragmatic development. 
  
keywords          : "conjunction, disjunction, implicatures, semantics, pragmatics, logical connectives, language, acquisition, development, children"
wordcount         : "X"

bibliography      : ["Jasbi-Frank-2019.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r global_options}
knitr::opts_chunk$set(fig.path='figs/',
                      echo=F, warning=F, cache=TRUE, 
                      message=F, fig.pos = "!h")
```

```{r load_packages}
library(grid)
library("papaja")
library(irr)
library(lme4)
library(gtable)
library(png)
library(jpeg)
library(ggplot2)
library(xtable)
library(tidyverse)
library(bootstrap)
library(ggthemes)
library(forcats)
```

```{r bootstrapping}
## for bootstrapping 95% confidence intervals
theta <- function(x,xdata) {mean(xdata[x])}
ci.low <- function(x) {
  quantile(bootstrap(1:length(x),1000,theta,x)$thetastar,.025)}
ci.high <- function(x) {
  quantile(bootstrap(1:length(x),1000,theta,x)$thetastar,.975)}
```

```{r preliminary_wrangling}
## reading the processed data
data_main <- read.csv("study2/2_processed_data/cardgame_data_processed.csv")

data_main <-
  data_main %>%
  filter(trial_type!= "X.YorZ", trial_type!= "XY.YorZ", trial_type!= "XY.YandZ") %>%
  separate(trial_type, c("Card", "Guess"), sep="\\.", remove=FALSE)

data_adults <-
  data_main %>%
  filter(age_category=="Adults")

data_children <-
  data_main %>%
  filter(age_category=="Children")

data_main_dv3 <- 
  data_main %>%
  filter(dv_type==3)

data_main_dv2 <-
  data_main %>%
  filter(dv_type==2)

n_adults <- data_adults$sid %>% unique() %>% length()  
n_adults2 <- filter(data_main_dv2, age_category=="Adults")$sid %>% unique() %>% length() 
n_adults3 <- filter(data_main_dv3, age_category=="Adults")$sid %>% unique() %>% length()
```

```{r eval=FALSE}

ternary_Age <- brm(response ~ trial_type * age_year + (trial_type * age_year|sid), 
                    family = categorical,
                    iter = 4000,
                    set_prior("normal(0,10)", class = "b"),
                    data=data_children)

data_study3 <- unite(data_study3, trial_type, Animal, Guess, sep=".", remove= FALSE)

binary_Age <- brm(as.numeric(tvjt) ~ trial_type * age + (1|id), 
                    family = binomial,
                    iter = 2000,
                    set_prior("normal(0,10)", class = "b"),
                    data=data_study3)

feedback_Age <- brm(feedback ~ trial_type * age + (1|id), 
                    family = categorical,
                    iter = 4000,
                    set_prior("normal(0,7)", class = "b"),
                    data=filter(data_study3,feedback!="0"))
```

<!--
To-Do:
* Read through the whole paper again
  - Explain that adults and children find A or B when only one is true still wrong exactly because the speaker could still say something simpler and more informative. Children's preference for disjunction with both disjuncts true over such cases may also be explained by the fact that they consider the correct detection of a coordination more important than incorrect choice of connective.
* Write a new conclusion
  - We conclude that using open-ended elicitation and analysis of children's feedback **together with** forced choice truth judgment tasks may provide us with better measurements of children's true semantic and pragmatic competence
* Spellcheck
-->

## Introduction

Disjunction has had a key role in advancing theories of logic, language, and cognition. When introducing disjunction to students of logic, Alfred @tarski1941logic complained about the complex factors that affect its comprehension in everyday language: 

>"the usage of the word *or* in everyday English is influenced by certain factors of a psychological character. Usually we affirm a disjunction of two sentences only if we believe that one of them is true but wonder which one. If, for example, we look upon a lawn in normal light, it will not enter our mind to say that the lawn is green or blue, since we are able to affirm something simpler, and at the same time, stronger, namely that the lawn is green. Sometimes even, we take the utterance of a disjunction as an admission by the speaker that he does not know which of the members of the disjunction is true." 

In addition to the \textsc{speaker ignorance} effect of *or*, Tarski noted that a disjunction has at least two different interpretations. For example, a child may ask us to be taken to a hike in the morning and a theater in the afternoon, but we may respond: "No, we are going on a hike or we are going to the theater". He explained that disjunction in this example is \textsc{exclusive} because "we intend to comply with only one of the two requests" and not both. However, a disjunction may also have an \textsc{inclusive} interpretation like the following example: "Customers who are teachers or college students are entitled to a special reduction". Tarski explained that *or* in this example is inclusive "since it is not intended to refuse reduction to a teacher who is at the same time a college student." Tarski explained that there are "quite noticeable differences between the usage of [disjunction] in everyday language and in logic" and that "the creators of contemporary logic, when introducing the word *or* into their considerations, desired, perhaps unconsciously, to simplify its meaning and to render the latter [logical disjunction] clear and independent of psychological factors." Some logicians and philosophers of language like P.F Strawson went even further and suggested that "ordinary language has no exact logic" [@strawson1950referring]. 

The idea that there are noticeable differences between logical and linguistic connectives remained common wisdom until H. Paul Grice's "logic and conversation" [@grice1975logic]. He contended that the perceived differences between the meaning of natural language connectives such as *or* and the semantics of logical operators such as $\vee$ (inclusive disjunction) "arise from inadequate attention to the nature and importance of the conditions governing conversation." He argued for two types of meaning: "what is said" and "what is (conversationally) implied". "What is said" refers to the literal meanings of words; the conventional association between words and meanings that is (relatively) context-independent. "What is (conversationally) implied" (i.e. \textsc{conversational implicature}), refers to meaning that is created by using words and sentences in context. He contended that conversation is governed by (at least) four maxims: be truthful (Maxim of Quality), be informative (Maxim of Quantity), be relevant (Maxim of Relevance), and be concise (Maxim of Manner). Conversational implicatures are refinements to the literal meanings of words to make sure that the utterance abides by the conversational maxims. As such, implicatures are rational inferences and derived via the interaction of literal meaning with conversational principles. In linguistics, the distinction between "what is said" and "what is implied" gave rise to two interrelated subfields in the study of meaning: semantics and pragmatics. 

Grice's main test case for his theory of meaning was the word *or*. He argued that the literal meaning of *or* (i.e. its semantics) is inclusive disjunction as defined in classical logic. However, this literal meaning is enriched in context to generate ignorance and exclusivity inferences. Grice generalized and systematized Tarski's intuition that we do not say "the lawn is green or blue" because we can say "something simpler" (abiding by the Maxim of Manner), and at the same time, stronger (abiding by the Maxim of Quantity): that "the lawn is green". Therefore, a disjunctive assertion commonly results in the inference that the speaker could not have uttered only one of the disjuncts, because s/he is uncertain about their truth (ignorance inference). Similarly, exclusivity of a disjunction is inferred by reasoning about the speaker's choice of the connective (*or* instead of *and*). Going back to Tarski's example, the child can reason that her dad could have said "we are going on a hike *and* we are going to the theater" if he intended to do both. He used *or* instead. Assuming he knows whether he wants to do both or not, his utterance must mean means he wants to do one or the other (exclusivity inference). Within the Gricean framework, ignorance and exclusivity of *or* are secondary inferences, derived from the interaction of its literal (inclusive) meaning with conversational principles. Grice's arguments gave rise to a radical methodological and theoretical shift in the study of meaning in philosophy and linguistics.

In psychology, disjunction and its related words such as the English *or* have played an important role in advancing theories of logical thought and its development in humans [@piaget1958growth; @neisser1962hierarchies]. Early studies tested adults and children's comprehension of logical words such as *and*, *or*, and *not* as a proxy for human logical understanding [@nitta1966basic;@neimarkSlotnick1970; @neimark1970]. Influenced by the arguments that language has no logic, researchers asked at what age logical (inclusive) and nonlogical (exclusive) understanding of disjunction develops. They arrived at the conclusion that while the logical meaning of conjunction and negation were understood early, the logical meaning of disjunction was a late development; in fact as late as highschool or college years. Advances and improvements in the methods used to test adults and children's linguistic comprehension convinced some researchers that the logical understanding of disjunction is present in school years, but not in preschool [@braine1981development]. 

The advent of the Gricean approach to meaning shifted the research question, from the development of logical and nonlogical concepts, to the development of the semantics and pragmatics of logical words. Some developmental researchers argued that by advancing methods that separate semantic from pragmatic competence in children, they show an early understanding for the truth conditions of linguistic connective *or* as inclusive disjunction [@chierchia1998some; chierchia2004semantic; @crain2012emergence]. According to @crain2012emergence, not only children's understanding of disjunction matches its semantics in classical logic, but it is also probable that this understanding is part of an innate logical endowment [@crain2008logic; @crain2010logic]. Since the start of research on children's development of disjunction, more than 30 research papers have been published on the topic and this number is sure to increase as research on disjunction sheds light on various aspects of human understanding and development of meaning and logic. 

The research presented here builds on this long and well-established literature in two ways. First, it further improves on previous experimental methods. Some previous experimental studies used complex experimental design, complex linguistic stimuli, or alternatively lacked appropriate controls such as a control connective or comprehension of adults in the same task. In section \@ref(litreview) we review these issues and in section \@ref(study1) we present an experimental paradigm that avoids them. Second, most previous research tested children and adults using two-alternative forced-choice tasks (2AFC) [@crain1998investigations]. Here, we report adults and children's judgments with both two and three alternatives (2AFC and 3AFC tasks). We also compare children's truth value judgments against their open-ended verbal feedback to the speaker.

Study 1 (section \@ref(study1)) tested adults' interpretations of connectives *and* and *or* in the context of a guessing game using 2AFC and 3AFC truth value judgment tasks. The 2AFC task showed that adults interpret *and* as conjunction and *or* as inclusive disjunction in the guessing game. The 2AFC task did not show sensitivity to the pragmatics of disjunction in the game. The 3AFC task, however, showed sensitivity to the pragmatics of disjunction: participants were more likely to pick the middle option among three alternatives, when both disjuncts were true. Comparing the 2AFC and 3AFC results, the 2AFC task underestimated judgments of felicity and better approximated truth judgments compared to the 3AFC task. This finding is intuitive given that more options provide a better opportunity to express nuances of linguistic interpretation.

Study 2 (section \@ref(study2)) investigated preschool children's judgments in the same guessing game as study 1 using a 3AFC task. We used three alternatives to give children a better chance of expressing their pragmatic knowledge and judgments of felicity [@katsos2011pragmatic]. The study also analyzed and categorized children's open-ended verbal feedback in the task. Both the 3AFC judgments and the categories of open-ended responses showed that four-year-olds differentiated *or* from *and*. While children's judgments in the 3AFC task showed no sign of infelicity for disjunctive guesses when both disjuncts were true, their open-ended feedback showed that children find such guesses infelicitous. In their open-ended feedback, children explicitly emphasized the word *and* as what the speaker (i.e. puppet) should have used instead of *or*, when both disjuncts were true.

Study 3 (section \@ref(study3)) used the same paradigm as study 2, but focused on replicating preschool children's open-ended responses and contrasting them with the results of a 2AFC task. As in study 2, both truth judgments and open-ended feedback showed that children differentiated *or* from *and*. The 2AFC task showed no evidence that children find disjunctions with true disjuncts infelicitous. However, children's judgments did not differ significantly from those of adults in the 2AFC task of study 1. As in study 2, children's open-ended feedback suggested that when both disjuncts were true, children found a disjunctive statement infelicitous and the conjunctive alternative more appropriate. Overall, the results of study 2 and 3 show that forced-choice judgement tasks underestimate children's pragmatic competence. In contrast, systematic analysis of children's open ended verbal feedback captured children's sensitivity to pragmatic violations. We conclude that using open-ended elicitation and analysis of children's feedback **together with** forced choice truth judgment tasks may provide us with better measurements of children's true semantic and pragmatic competence.

## Previous Research{#litreview}

Research on children's comprehension of logical connectives *and* and *or* consists of two periods. The first period (1960s-80s) was inspired by Piaget's developmental theory [@piaget1958growth]. Researchers in this period sought to discover the development of basic logical concepts such as negation, conjunction, and disjunction. Following @piaget1958growth, they predicted that children first form concrete concepts for conjunction and disjunction between the ages of 7-11 years (concrete operational stage) and only after 11 (formal operational stage) do they develop an abstract and logical understanding of these words. While later research in this period rejected this timeline, it upheld the claim that a logical (inclusive) understanding of disjunction develops late. The second period (since late 90s) is inspired by Grice's theory of meaning, specifically his distinction between semantics and pragmatics. Researchers in this period argued that previous studies conflated semantic and pragmatic knowledge and used methods that vastly underestimated children' semantic competence. By controlling for the role of pragmatics and focusing on children's truth judgments, they aimed to show that children have early and adult-like semantics for logical words such as *or*. Based on these results, they argued that the understanding of logical concepts and their role in language is likely innate [@crain2008logic;@crain2010logic]. In what follows, we review the highlights of these two traditions and end with a note on how the studies presented here contribute to this long-standing research on development of disjunction.

To examine the Piagetian theory, @nitta1966basic tested 679 Japanese students (grades K, 2, 4, 6, and 8) and @neimarkSlotnick1970 conducted a similar study on 455 English-speaking children in grades 3-8 and 58 college students. Participants were tested on negation, conjunction, and disjunction. Each question provided six response options; for example a fish, a bird, and a flower, each with a white and a black version. Participants were asked to "circle all the items" described by statements such as: "flower", "not bird", "bird and flower", "bird or flower", "black and bird", "black or flower", etc. These studies concluded that the majority of the participants understood negation and conjunction, but only college students correctly answered statements containing a disjunction. They reported that participants made two types of errors. First across all ages, some participants interpreted disjunction as conjunction. For example they circled black birds when the instruction said "black or bird". Second, some selected only one of the two categories. Based on these results @neimark1970 concluded that a "correct" (i.e. inclusive) understanding of disjunction only develops in the high school years and depends on the attainment of formal operations as defined in the Piagetian theory.

@paris1973comprehension used a similar in-classroom setup to test children's comprehension of connectives in Grades 2, 5, 8, 11, and college. Two hundred participants (40 per grade) were asked to judge the truth of sentences with the connectives *and*, *or*, and *either-or*. The experimenter showed participants slides of pictures, for example a bird in a nest, with descriptions such as "the bird is in the nest or the shoe is on the foot." The participants were asked to judge the statement as true or false. Paris found that statements with *and* were almost always judged correctly, but this was not the case with disjunction. First, he reported that older participants produced more errors when both disjuncts were true, presumably because they interpreted disjunctions as exclusive and not inclusive. Second, the majority of younger children, and even around a fifth of college students considered a disjunction false when only one of the disjuncts was true. The combination of these two trends suggested that younger children and even some adults did not differentiate *or* from *and*, interpreting both as conjunction. Finally, Paris also found that there were fewer errors with *either-or* statements compared to *or* statements. He suggested that the word *either* could provide further cue on how disjunction should be interpreted. @paris1973comprehension attributed the conjunctive interpretations of *or* to the application of non-linguistic strategies when an utterance is hard to interpret [See @clark1973non for a discussion of nonlinguistic strategies in child language acquisition]. He suggested that children in his task were "comparing visual and auditory information with little regard for the implied logical relationship in the verbal description." In other words, children responded with "true" if the individual disjuncts matched the pictures and false otherwise. Such a non-linguistic strategy would yield correct answers for conjunction but incorrect (conjunctive) answers for disjunction. This explains why conjunctive readings reduce with age and why using the word *either* helped reduce conjunctive interpretations further.

After @paris1973comprehension, it was understood that the in-class tests were not suitable for testing participants' linguistic competence and certainly not suitable for younger children. Therefore, @johansson1975preschool set out to examine the interpretation of disjunction in a simpler "Give-item" task. They tested preschool Swedish-speaking children's comprehension of conjunction and disjunction in present tense sentences (e.g. "Richard wants to drink lemonade or milk. Show me what he drank!") and imperative sentences (e.g. "Put up [the picture of] the car or the doll!"). They reported that starting (at least) at age four, children interpreted the Swedish equivalents of *and* and *or* as conjunction and exclusive disjunction. They argued that the linguistic *or* should be kept separate from the logical notion of (inclusive) disjunction. While linguistic understanding of *or* develops early as exclusive disjunction, the logical understanding of it develops late. 

@braine1981development is the only study that tested the same participants with both a Give-item task and a version of what is today known as the Truth Value Judgment Task. They tested 22 children in each of the age groups 5-6, 7-8, and 9-10 years, as well as 22 adults. In the Give-item task, 14 wooden blocks with varying shapes, colors, and sizes were used [a replication of @suppes1969young]. Experimenters asked participants the following: 1) "Give me all the green things or give me all the round things" and 2) "Give me all those things that are either blue or round." They reported that for both commands and in both children and adults, the most likely response was to give all the objects that had only one of the properties. They considered these results as evidence for a "choose-one" (i.e. exclusive) interpretation of disjunction in the context of imperatives. 
In the judgment task, a puppet described the contents of four boxes that each contained four animal toys. For example, the puppet said "Either there is a horse or a duck in the box." The first box had both animals, the second had only a horse, the third only a duck, and the last had neither. Participants were asked if the puppet was right. The results showed that adults were split between an inclusive and an exclusive interpretation of disjunction. The 7-8 and 9-10 year-olds were more likely to consider the disjunction as inclusive. However, the youngest group (5-6 years old) was most likely to interpret a disjunction similar to a conjunction: they said the puppet was right when both animals were in the box and not right or partly right if only one of the animals was in the box. Following @paris1973comprehension, @braine1981development argued that younger children do not take the contribution of the connective *or* into account. Instead, they use a non-linguistic strategy in which the disjunction is right if both propositions are true, partly right if only one is true, and wrong if neither is true.

@braine1981development concluded that children's ability to interpret a disjunction in a command develops earlier than their ability to judge truth values. It is important to note that in @braine1981development's judgment task, the puppet used a disjunction even though the content of the box was known to both the puppet and the participant (i.e. it lacked ignorance). As @tarski1941logic noted, such uses of disjunction sound odd and infelicitous. More generally, a disjunction such as "A or B" is infelicitous when discourse participants already know which proposition is true. Later truth value judgment studies such as @chierchia1998some controlled for this effect of disjunction by making the puppet utter disjunction as a prediction of an unknown event, and let participants judge the prediction after they see the outcome of the event. 

@chierchia1998some kicked off the second period of inquiry into children's comprehension of disjunction. Following @grice1989studies, they differentiated between semantic knowledge, which includes the knowledge of truth values, and pragmatic knowledge. They contended that interpreting logical connectives involves a semantic and a pragmatic component, and that the semantics of logical connectives cannot be assessed if the role of pragmatics is not controlled for. More specifically, they argued that felicitous use of a disjunction requires: (i) a set of alternatives  (ii) evidence that one of them holds (iiia) evidence that not all of them hold, or (iiib) uncertainty as to whether all of them hold. While the semantics of *or* is inclusive, a variety of factors including pragmatic reasoning can provide evidence that not all alternatives hold. For example, we may reason that given speaker's knowledge of the situation, they could have used the connective *and* if all alternatives were true. Therefore, to understand the semantic contribution of disjunction, we should test participants in contexts which are stripped from pragmatic factors that contribute to exclusivity. 

@chierchia1998some tested 23 English-speaking and 10 Italian-speaking children in two conditions: description mode and prediction mode. In both conditions, a troll considered whether to eat a hamburger, a piece of pizza, or an ice-cream and went ahead to eat a piece of pizza and an ice-cream but not a hamburger. In description mode, Kermit described what happened as "A troll ate a piece of pizza or an ice cream" while in prediction mode, Kermit used the same sentence as a prediction before the troll eats his lunch. They reported that in the description mode, children accepted Kermit's statement when both disjuncts were true less than one-third of the time. However, in prediction mode, they accepted such sentences 100% of the time. They argued that when we control for the effect of pragmatics on interpretation, children understand disjunction as inclusive, and conform to the semantics of disjunction in classical logic.

Following @chierchia1998some, several studies have argued that preschool children's knowledge of disjunction conforms to the predictions of classical logic and formal semantics in environments as varied as negative sentences [@crain2000acquisition], conditional sentences [@gualmini2000], restriction and nuclear scope of the universal quantifier *every* [@chierchia2001acquisition; @chierchia2004semantic], nuclear scope of the negative quantifier *none* [@gualminicrain2002], restriction and nuclear scope of *not every* [@notley2012notevery], and prepositional phrases headed by *before* [@notley2012children], as well as similar environments in other languages such as Mandarin Chinese and Japanese [@goro2004acquisition; @su2013disjunction; @su2014acquisition]. These studies also commonly reported that in linguistic environments where adults consider a disjunction exclusive, children are more likely to consider it inclusive. Since under the Gricean account, exclusive interpretation of disjunction is the result of pragmatic (scalar) implicatures, these findings are considered as further evidence for the hypothesis that young children do not compute implicatures at the rate that adults do [@noveck2001children; @papafragou2003scalar; @barner2011accessing].

It is important to note that all the studies mentioned above in the Gricean period use the Truth Value Judgment Task [@crain1998investigations]. As mentioned earlier, @braine1981development found that the same children were more likely to interpret a disjunction as exclusive in a give-item task and inclusive/conjunctive in a truth value judgment task. Therefore, it is possible that truth value judgment tasks are simply not suitable for capturing children' knowledge of exclusivity implicatures. Furthermore, several studies listed above test children's knowledge of disjunction in environments that largely collapse the distinction between *and* and *or*. For example, in the restriction of *every*, a conjunction and a disjunction can result in the same interpretation (e.g. *Every man or woman is happy* vs. *Every man and woman is happy*). Therefore, successful interpretation in these studies can also be achieved by applying the nonlinguistic strategies that result in conjunctive interpretations, as discussed by the early studies [@paris1973comprehension; @braine1981development].

More recently, some studies have revived the earlier findings that preschool children may interpret disjunction as conjunction. @Singh2016 tested 56 English-speaking children (M=4;11, 3;9-6;4) and 26 adults in a truth value judgment task. The experiment involved four pictures: a boy holding a banana, a boy holding an apple and a banana, three boys holding either an apple or a banana, and three boys holding both apples and bananas. In each trial, participants saw one of the pictures and a puppet described the pictures with four possible utterances: "The/every boy is holding an apple or/and a banana." Participants were asked: "Was [the puppet] right or wrong about this picture?" They found that children were more likely to say the puppet was right when both disjuncts were true than when only one was. They concluded that "many preschool children - the majority in [the study's] sample - understand disjunctive sentences ... as if they were conjunctions." 
@tieu2016 also found evidence for conjunctive interpretations of disjunction in preschool children. They tested 28 French-speaking children (3;7-6;6, M=4;5) and 18 Japanese-speaking children (4;7-6;6, M=5;5) as well as 20 French-speaking and 21 Japanese-speaking adults. They used the "prediction mode" of the Truth Value Judgment Task, in which the puppet provides a prediction or guess, an event occurs, and participants are asked if the prediction was right. For example, there was a chicken on the screen, next to a toy bus and a toy plane. The puppet appeared on the screen and predicted that "the chicken pushed the bus or the plane." Then the chicken pushed either one or both of the objects. Participants stamped on a happy face or a sad face to show whether the puppet's guess was right or wrong. Like @Singh2016, they reported that unlike adults, children were more likely to consider the disjunctive guess right when both disjuncts were true, rather than only one. They concluded that children - the majority of them in their sample - interpreted disjunction as conjunction. 

However, a recent replication of @tieu2016 by @skordosEtal2018 suggests that the high rate of conjunctive interpretations were most likely due to experimental design. They tested 126 preschoolers in three conditions: replication (N=43, 4;0-5;9, M=5;0), modified script (N=41, 4;0-5;10, M=5;0), and three-alternatives (N=42, 4;0-5;11, M=5;0). The first condition was a direct replication of @tieu2016. The second, modified script, removed some experimenter comments right after the puppet's guess that could potentially confuse children. The comments were: "Look! The chicken pushed that! She didn't want to break that one. So she didn't touch it. So was [the puppet] right?" The third condition, three-alternatives, was similar to modified-script but provided three objects; for example a plane, a bus, and a bicycle. The reasoning was that if there are only two alternatives, a disjunction is trivially true, and consequently children may consider that unacceptable. The results replicated @tieu2016's findings in the replication condition, but showed that conjunctive interpretations of disjunction disappeared almost completely in the third condition with three alternatives. @skordosEtal2018 concluded that children's conjunctive interpretations are most likely due to non-linguistic strategies applied when they are uncertain about some aspect of the experimental task. This conclusion is similar to the conclusions of @paris1973comprehension and @braine1981development in earlier studies. 

To summarize, previous studies show that experimental tasks can have a big impact on our conclusions regarding children's comprehension of disjunction. Early in-class tasks suggested that even high-schoolers do not interpret a disjunction correctly and confuse it with *and*. Improving on task design, @braine1981development argued that this is only the case in preschool children. They also showed that the same children can have different interpretations of disjunction in different tasks: in a Give-item task they interpret it as exclusive while in a truth value judgment task they interpret it as conjunctive or inclusive. Using various versions of the truth value judgment task, research in the Gricean tradition has argued that preschool children understand the semantics of disjunction and interpret it as inclusive. However, this line of research has also suggested that children are insensitive to the exclusivity implicature of disjunction. While some recent studies have argued that preschool children may interpret disjunction as conjunctive, a replication study has argued that conjunctive interpretations were largely due to task demands. 

Here we improve on previous studies by first controlling for various factors that had proven problematic before, and second investigating the role of task measurement in assessing preschool children's interpretation of disjunction. As explained above, previous research has shown that in studying children's interpretation of disjunction, it is important to control for the following factors:

1. complexity of the linguistic stimuli, 
2. complexity of the task,
3. ignorance of the speaker with respect to the truth of the disjuncts, 
4. interpretation of the conjunction word (e.g. *and*) in the same task
5. interpretation of adults in the same task. 
6. discernibility of conjunctive and disjunctive interpretations in the task

Some previous studies used complex linguistic stimuli or relatively complex designs that may have increased the application of non-linguistic strategies. Some studies violated "speaker ignorance"; i.e. had the speaker utter the disjunction when the truth of the propositions were known to the speaker. Some studies did not use the conjunction word (e.g. *and*) in control trials, or did not use adults as control participants. Finally, some studies tested the disjunction word in linguistic environments that collapse interpretive differences between a conjunction a disjunction. The experimental paradigm reported here builds and improves on previous studies by controlling for all these factors.

In the studies reported here, we used simple existential sentences (e.g. *there is a cat or a dog*) and tested the interpretation of participants in a simple and easy to understand guessing game. The guessing game provided a context in which the speaker was ignorant with respect to to which alternatives were true. The game is essentially a variant of the truth value judgment task and used conjunction trials as well as adult participants as controls. Conjunction and disjunction trials resulted in different interpretations in the task. Furthermore, we tested children's interpretations in two different ways, using forced choice tasks with 2 and 3 options (2AFC and 3AFC tasks), as well as free-form verbal responses.  

## Study 1: Adult's 2AFC and 3AFC Judgments{#study1}

The goal of this study was to examine adults' interpretations of *and* and *or* as a benchmark for children's interpretations. Participants saw a card, read a description, and had to evaluate the description with respect to what they saw on the card. In test trials, the descriptions contained the conjunction word *and* and the disjunction word *or*. We tested adults in both two-alternative and three-alternative forced choice tasks (2AFC and 3AFC). The results suggested that adults interpreted *and* as conjunction and *or* as inclusive disjunction. Adults also considered statements with *or* infelicitous when both disjuncts were true. The study also found that the 2AFC and 3AFC tasks registered different aspects of adult interpretations: the 2AFC task captured adult intuitions on the basic semantics of the connectives while the 3AFC task was sensitive to pragmatic infelicities as well.

### Methods

#### Materials and Design

```{r stimuli, fig.env = "figure", fig.align='center', fig.width=2, fig.cap = "Cards used in the connective guessing game."}
cards_img <- jpeg::readJPEG("study1/0_methods/Stimuli/cards.jpg")
grid::grid.raster(cards_img)
```

We used six cards with cartoon images of a cat, a dog, and an elephant (Figure \@ref(fig:stimuli)). There were two types of cards: cards with only one animal and cards with two animals. There were three types of guesses: simple (e.g. *There is a cat*), conjunctive (e.g. *There is a cat and a dog*), and disjunctive (e.g. *There is a cat or a dog*). In each guess, the animal labels used in the guess and the animal images on the card could have no overlap (e.g. Image: dog, Guess: *There is a cat or an elephant*), partial overlap (e.g. Image: Cat, Guess: *There is a cat or an elephant*), or total overlap (e.g. Image: cat and elephant, Guess: *There is a cat or an elephant*). Crossing the number of animals on the card, the types of guesses, and the overlap between the guess and the card yields 12 different possible trial types. We chose 8 trial types (Figure \@ref(fig:trials)), to balance the number of one-animal vs. two-animal cards, simple vs. connective guesses, and expected true vs. false trials.

```{r trials, fig.env = "figure", fig.align='center', fig.width=3, fig.cap = "Trial types represented by example cards and example guesses."}
trials_img <- jpeg::readJPEG("figs/trial-types.jpg")
grid::grid.raster(trials_img)
```

#### Participants and Procedure

```{r exampleTrial, fig.env = "figure", fig.align='center', fig.width=2, fig.cap = "An example trial in Study 1."}
trial_img <- jpeg::readJPEG("figs/example_trial.jpg")
grid::grid.raster(trial_img)
```

We used Amazon’s Mechanical Turk (MTurk) for recruitment and the online platform Qualtrics for data collection and survey design. The task took about 5 minutes on average to complete. `r n_adults` English speaking adults participated. `r n_adults2` of them were assigned to a 2AFC judgment task and `r n_adults3` to a 3AFC judgment task. In the 2AFC task, participants had to judge using the options "wrong" and "right". In the 3AFC task they had to choose between "wrong", "kinda right", and "right". The two conditions were otherwise identical. There are many possible labels for the middle option "kinda right", including "kinda wrong" or "neither". A later experiment, tested different intermediate labels and found that adults consider "kinda right" to be a more suitable option for capturing pragmatic infelicities [ see @jasbiWaldonDegan2017]. We expect similar behavior from labels like "a bit right" and "a little right" which refer to non-maximal degrees of being "right". 

The experiment had three phases: introduction, instruction, and test. In the introduction, participants saw the six cards and read that they would play a guessing game. Then a blindfolded cartoon character named Bob appeared on the screen. Participants were told that in each round of the game, they would see a card and Bob was going to guess what animal was on the card. The study emphasized that Bob could not see anything. Participants were asked to judge whether Bob's guess was right. In the instruction phase, participants saw an example trial where a card with the image of a dog was shown with the following sentence written above Bob's head: *There is a cat on the card*. All participants correctly responded with "wrong" and proceeded to the test phase.

In the test phase, participants saw one trial per trial type. Within each trial type, the specific card-guess scenario was chosen at random. The order of trial types was also randomized. At the end of the study, participants received $0.4 as compensation. Figure \@ref(fig:exampleTrial) shows an example test trial.

Study | N | Age | Mode | Response Options |
|---|---|---|---|---|
Study 1 - 2AFC | `r n_adults2`| Adults | Online (Mturk) | Wrong, Right|
Study 1 - 3AFC | `r n_adults3`| Adults | Online (Mturk) | Wrong, Kinda Right, Right|
Table:(\#tab:study1info)Summary of study 1 methods with adult participants 

### Results 

In this section, we first present the results of the 2AFC and 3AFC tasks with adults. Then we discuss how these results can be interpreted with respect to the semantics and pragmatics of disjunction in the context of the guessing game.

```{r plots}
prop_table <- 
  data_main %>% 
  group_by(sid, Card, Guess, age_category, dv_type, response) %>%
  summarise(counts= n()) %>%
  spread(response, counts) %>%
  replace(is.na(.), 0) %>%
  mutate(total = Wrong + Right + `Kinda Right`) %>%
  gather(response, counts, `Kinda Right`:Wrong) %>%
  mutate(prop = counts / total) %>%
  group_by(Card, Guess, age_category, dv_type, response) %>%
  summarize(cih = ci.high(prop),
            cil = ci.low(prop),
            prop = mean(prop))

# order the levels as Wrong, Kinda Right, and Right
prop_table$response <- relevel(as.factor(prop_table$response), ref="Wrong")

prop_table$Guess <- fct_recode(prop_table$Guess,  Z="Y")

prop_table  <- rename(prop_table, Options = dv_type, `Age Category` = age_category)

prop_table$Guess <- 
  prop_table$Guess %>%
  factor(levels = c("Z", "X", "YandZ", "YorZ", "XandY", "XorY")) %>%
  fct_recode(Elephant = "Z", Cat = "X", `Cat and Dog`="XandY", `Cat or Dog`="XorY", `Dog and Elephant` = "YandZ", `Cat or Elephant` = "YorZ")
```

```{r binaryAdultsPlot, fig.env = "figure", fig.width=6, fig.height=4, fig.cap = "Adults' two-alternative forced choice judgments."}
adults_plot2<-
  prop_table %>%
  filter(Options==2, `Age Category`=="Adults") %>%
  filter(response!="Kinda Right") %>%
  ggplot(aes(x=response, y=prop, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(Card~Guess) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=11, family="Times")) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

cat <- 
  readJPEG("study1/0_methods/stimuli/cat_card.jpg") %>%
  rasterGrob(width=0.9)

cat_dog <- 
  readJPEG("study1/0_methods/stimuli/catdog_card.jpg")%>%
  rasterGrob(width=0.9)

adults_plot_g <- ggplot_gtable(ggplot_build(adults_plot2))

strips <- grep("strip-r", adults_plot_g$layout$name)

new_grobs <- list(cat, cat_dog)

adults_plot_g <- with(adults_plot_g$layout[strips,],
          gtable_add_grob(adults_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

adults_plot_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(adults_plot_g)
```

Figure \@ref(fig:binaryAdultsPlot) shows the results for the adult 2AFC task. The two left columns show the simple guesses and serve as controls. The results show that if the animal mentioned in the guess was not on the card (e.g., elephant), participants judged the guess to be "wrong"; if the animal was on the card (e.g., cat), participants judged the guess to be "right". The next two columns of Figure \@ref(fig:binaryAdultsPlot) show the results for the test conditions, namely conjunction and disjunction. An *and*-guess (e.g. cat and dog) was considered "wrong" if only one of the animals was on the card, and "right" if both were. An *or*-guess (e.g. cat or dog) was "right" whether one or both animals were on the card. The patterns of "right" and "wrong" responses in the binary task match the expectations for truth and falsehood of logical conjunction and (inclusive) disjunction.

```{r ternaryAdultsPlot, fig.env = "figure", fig.width=6, fig.height=4, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}
adults_plot3<-
  prop_table %>%
  filter(Options==3, `Age Category`=="Adults") %>%
  ggplot(aes(x=response, y=prop, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(Card~Guess) +
  labs(x="", y="")+
  theme_few() +
  theme(axis.text.x = element_text(angle=45, hjust = 1, vjust = 1), text = element_text(size=11, family="Times")) +
  scale_fill_manual(values = c("red4", "grey","springgreen3"), guide=FALSE)

cat <- 
  readJPEG("study1/0_methods/stimuli/cat_card.jpg") %>%
  rasterGrob(width=0.9)

cat_dog <- 
  readJPEG("study1/0_methods/stimuli/catdog_card.jpg")%>%
  rasterGrob(width=0.9)

adults_plot_g <- ggplot_gtable(ggplot_build(adults_plot3))

strips <- grep("strip-r", adults_plot_g$layout$name)

new_grobs <- list(cat, cat_dog)

adults_plot_g <- with(adults_plot_g$layout[strips,],
          gtable_add_grob(adults_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

adults_plot_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(adults_plot_g)
```

```{r Study1TernaryStats}
responses_XY_X_3 <- filter(data_adults, dv_type==3, trial_type=="XY.X")$response
  
XY_X_3_binomTest <-binom.test(x=table(responses_XY_X_3)[1], n=length(responses_XY_X_3), p=0.5, alternative = "greater", conf.level = 0.95)

responses_X_XoY_3 <- filter(data_adults, dv_type==3, trial_type=="X.XorY")$response
  
X_XoY_3_binomTest <-binom.test(x=table(responses_X_XoY_3)[2], n=length(responses_X_XoY_3), p=0.5, alternative = "greater", conf.level = 0.95)

responses_X_XnY_3 <- filter(data_adults, dv_type==3, trial_type=="X.XandY")$response

X_XnY_3_binomTest <-binom.test(x=table(responses_X_XnY_3)[3], n=length(responses_X_XnY_3), p=0.5, alternative = "greater", conf.level = 0.95)

responses_XY_XoY_3 <- filter(data_adults, dv_type==3, trial_type=="XY.XorY")$response

XY_XoY_3_binomTest <-binom.test(x=table(responses_XY_XoY_3)[1], n=length(responses_XY_XoY_3), p=0.5, alternative = "greater", conf.level = 0.95)
```

Figure \@ref(fig:ternaryAdultsPlot) shows the results for the 3AFC judgment task. For four trial types, the results were identical to the 2AFC task. In the first and second trial types, if the animal mentioned was not on the card (e.g. elephant), participants judged the guess as "wrong", regardless of whether one animal was on the card or two. In the third trial type, if the animal mentioned (e.g. cat) was the only animal on the card, participants judged the guess as "right". Finally, if there were two animals on the card and the puppet mentioned them using *and* (e.g. cat and dog), all participants considered the guess "right".

The four remaining trial types showed different patterns of judgments than their counterparts in the 2AFC task. If the animal mentioned (e.g. cat) was only one of the animals on the card, participant judgments were divided between "right" and "kinda right"<!--(See Table \@ref(tab:binomStats), row 1 for a binomial test)-->. When only one of the animals was on the card (e.g. cat) and the guess was a conjunction (e.g cat and dog), most adults considered the guess "wrong" but some chose "kinda right", perhaps suggesting that the intermediate option was used to express that one of the animals was correctly guessed. With disjunctive guesses (e.g. cat or dog), if the card had only one of the animals (e.g. cat), most participants considered the guess "right" while some considered it "kinda right". It is possible that those who chose "kinda right" considered the right guess to be "cat". For disjunctive trials with both animals on the card, adults were split between "kinda right" and "right" responses. The choice of "kinda right" over "right" in such trials can be interpreted as a sign that adults were sensitive to the infelicity of a disjunction when conjunction was more appropriate. In the next section, we discuss the nature of pragmatic reasoning in the context of this guessing game.
<!--
|Trial Type | $n_{_{right}}/n_{_{total}}$ | $\hat{p}_{_{right}}$ | $p_{_{null}}$ | p-value | $95\%~CI$|
|--------------------------|-------------|------|------|------|---------------|------|
|Two Animals - Simple | `r table(responses_XY_X_3)[1]`/`r length(responses_XY_X_3)` | `r round(XY_X_3_binomTest$estimate,2)` | `r XY_X_3_binomTest$null.value` | `r round(XY_X_3_binomTest$p.value, 2)`| `r round(XY_X_3_binomTest$conf.int[1],2)`-`r round(XY_X_3_binomTest$conf.int[2],2)`|
|One Animal - AND | `r table(responses_X_XnY_3)[1]`/`r length(responses_X_XnY_3)`| `r round(X_XnY_3_binomTest$estimate,2)` | `r X_XnY_3_binomTest$null.value` | `r round(X_XnY_3_binomTest$p.value, 3)` |`r round(X_XnY_3_binomTest$conf.int[1],2)`-`r round(X_XnY_3_binomTest$conf.int[2],2)`|
|One Animal - OR| `r table(responses_X_XoY_3)[1]`/`r length(responses_X_XoY_3)` |`r round(X_XoY_3_binomTest$estimate,2)` | `r X_XoY_3_binomTest$null.value` | `r round(X_XoY_3_binomTest$p.value, 2)` | `r round(X_XoY_3_binomTest$conf.int[1],2)`-`r round(X_XoY_3_binomTest$conf.int[2],2)`|
|Two Animals - OR|`r table(responses_XY_XoY_3)[1]`/`r length(responses_XY_XoY_3)`|`r round(XY_XoY_3_binomTest$estimate,2)`|`r XY_XoY_3_binomTest$null.value`|`r round(XY_XoY_3_binomTest$p.value, 2)`|`r round(XY_XoY_3_binomTest$conf.int[1],2)`-`r round(XY_XoY_3_binomTest$conf.int[2],2)`|

Table: (\#tab:binomStats) Exact One-Sided Binomial Test
-->

### Discussion

Consider the following truth conditions for *and* and *or*: A conjunction with *and* is true when both conjuncts are true and false otherwise. An inclusive disjunction with *or* is true when at least one disjunct is true and false otherwise. An exclusive disjunction is true when only one of the disjuncts is true and false otherwise. Let's also assume a simple linking function in which false statements are judged as "wrong" and true statements as "right" (see @jasbiWaldonDegan2017 for a discussion of linking assumptions in this task). In the context of study 1, this purely truth-conditional account has the following predictions: First, conjunctive guesses like "cat and dog" are wrong when only one of the animals is on the card and right when both are. Second, disjunctive guesses are always right if they are interpreted as inclusive, because in all such trials at least one of the animals is present on the card. However, if disjunctive guesses are exclusive, they are right when one of the animals is on the card and wrong when both are. Finally, the addition of a third intermediate option between wrong and right should not substantially affect the judgments. 

Figure \@ref(fig:binaryAdultsPlot) shows that in 2AFC judgments, the predictions are borne out for *and* as conjunction and *or* as inclusive disjunction, but not exclusive disjunction. The majority of disjunctive guesses were considered right in the 2AFC task and in the 3AFC task, no disjunctive guess was judged wrong. These results suggest that inclusive disjunction better captures the truth-conditions of *or* in the existential sentences of this paradigm. However, in the 3AFC task, judgments deviated from a purely truth-conditional account in four trial types: (i) trials with simple guesses when two animals were shown on the card; (ii) disjunction trials with one animal; (iii) disjunction trials with two animals; and (iv) conjunction trials with one animal on the card. 

These trial types fall into two major categories with respect to their response patterns. First, those in which participants chose "kinda right" and "right" (i-iii); Second, those in which participants chose "wrong" and "kinda right" (iv). The first category corresponds to trial types in which the guesses were literally true, but pragmatically infelicitous. In trial types (i) to (iii), there were always better alternative guesses. When there were two animals on the card (e.g. cat and dog), a guess mentioning only one of them (e.g. there is a cat) was technically true but a better guess would have been one mentioning both animals with *and* (e.g. cat and dog). This was also the case for disjunctive guesses (e.g. cat or dog) when both animals were on the card. When only one animal was on the card (e.g. cat), a simple guess (e.g. there is a cat) was more appropriate than a disjunctive one (e.g. there is a cat or a dog), even though a disjunctive guess is literally true.

The second category of responses, namely "wrong" and "kinda right", only happened in one trial type: when there was one animal on the card (e.g. cat) and the guess was a conjunction (e.g. cat and dog). While the majority of participants considered such guesses as "wrong", some considered them not as bad as failing to name any of the animals on the card. In other words, the pattern of judgments captured the fact that such conjunctive guesses correctly name one of the animals on the card but not both. Overall, the comparison of forced choice judgments with two and three alternatives suggests that two alternatives better captured the truth-conditional meaning of the connectives, but underestimated adult pragmatic reasoning in the guessing game.

<!--
```{r scalarTests}
data_adults$binary_response <- fct_recode(data_adults$response, Wrong = "Kinda Right")

or_trials <- filter (data_adults, trial_type == "X.XorY" | trial_type == "XY.XorY")

disjunctTrialsModel <- summary(glmer(binary_response ~ trial_type + (1 + trial_type|sid), family= "binomial", data=filter(or_trials, dv_type==3)))
```

```{r exclusivity, fig.env = "figure", fig.width=2.5, fig.cap = "Example of cards referred to by a conjunction, inclusive disjunction, and exclusive disjunction."}
excl_diagram <- jpeg::readJPEG("figs/exclusivity_diagram.jpg")
grid::grid.raster(excl_diagram)
```

A disjunctive assertion like "cat or dog" gives rise to an ignorance inference and an exclusivity inference. The ignorance inference is the inference that the speaker does not know which disjunct actually holds. For example in figure \@ref(fig:exclusivity), the disjunctive guess is uncertain between three outcomes: cards 1, 2, and 3. A disjunction is infelicitous when the outcome is known to discourse participants. The guessing game in this study controls for this ignorance effect by keeping the guesser blindfolded. Therefore, all the disjunctive guesses are evaluated in a context where participants know that the guesser is ignorant of the animals on the cards - both the number of them on the card and their identity. The exclusivity inference is the inference that only one of the disjuncts holds and **not both**. In figure \@ref(fig:exclusivity), a disjunction like "cat or dog" only refers to cards 2 and 3 if it is accompanied by an exclusivity inference. 

Since @grice1989studies, this exclusive interpretation of *or* has been (at least partly) attributed to pragmatic reasoning about the speaker's connective choice. The reasoning goes like this: conversational participants are required to make their utterances as informative as possible. In the context of making predictions and guessing, a guesser is required to make any guess as specific (i.e. informative) as possible. [^7] A conjunction is more specific and informative than a disjunction [@horn1989natural]. For example in Figure \@ref(fig:exclusivity), *cat and dog* picks card 1 while *cat or dog* refers to cards 1, 2, and 3. If speakers intend to refer to card 1, they should use *and* and say *cat and dog*. If they use *or* instead of *and*, they probably do not intend to refer to card 1. Following this line of reasoning, we can exclude the possibility that a speaker intends to refer to card 1. The term "exclusivity implicature" captures this pragmatic reasoning that results in excluding the possibility of both disjuncts being true. 

[^7]: When you ask someone to predict the outcome of a coin toss, a guess like "it will be heads or tails" does not count as a felicitous guess or prediction, presumably because it is not informative, ie.e. it will always be true.

There are three main components to the pragmatic reasoning in the guessing game: 1. the assumptions of the game. 2. sensitivity to (under)informativity, and 3. the pragmatic reasoning about the speaker's choice of connectives. Like Katsos \& Bishop [-@katsos2011pragmatic], we have considered "sensitivity to informativeness" as a precondition for "derivation of scalar implicatures". We begin with the assumptions of the guessing game.

* **Guessing Game Assumptions**:
    + **Ignorance**: the guesser does not know the number or identity of the animals on the card.
    + **Specificity**: the guesser is required to be as specific as possible, ideally referring to a single card.

As explained before, ignorance of the guesser was explicit and part of the instructions in the study. However, specificity was an implicit assumption[^8]. All the guesses used in the experiment can pick a single card except for disjunctive ones. Conjunctive guesses like *cat and dog* pick specific cards. The simple ones like *cat* can be strengthened pragmatically to mean "only a cat", and pick a specific card. However, Disjunctive ones like *cat or dog* pick two cards in their most specific (exclusive) sense. Therefore, they are always under-informative and violate the specificity assumption.

* **Sensitivity to Informativeness**: The guesser said *cat or dog* which is under-informative and picks cards 1, 2, and 3.

* **Violation Assumption**: the guesser is violating the specificity requirement.

Participants can detect the underinformativity of disjunctive guesses, notice the violation of specificity, and then decide whether they would like to tolerate this violation or punish it. It should be pointed out that it is hard to distinguish between "tolerating the specificity violation" and simply revising the specificity assumption of the game to avoid a violation. For example, participants may assume that the goal of the game is saying something true about the cards rather than being as specific as possible. In either case, the prediction is that adults who tolerate violation or revise specificity would judge disjunctive guesses as "right". However, if participants assume specificity and decide to not tolerate its violation, they will judge all disjunctive guesses to have some degree of infelicity. Since an under-informative guess is still technically correct, participants may not punish such a guess with a "wrong" response and prefer an intermediate option like "kinda right". This is what study 1 shows. With two alternatives, not many adults judge infelicity with disjunctive guesses and there are almost no "wrong" responses. With three alternatives, "kinda right" responses pop up. Adult responses are split between "kinda right" and "right". 

```{r implicaturePlot, fig.env="figure", fig.cap="Adult responses to disjunction guesses like \\textit{cat or dog} with 2 and 3 options."}
disjunctionPlot <-
  prop_table %>%
  filter(Guess=="Cat or Dog", `Age Category`=="Adults") %>%
  ggplot(aes(x=response, y=prop)) +
  geom_bar(stat = "identity") +
  facet_grid(Card ~ Options, scales = "free", drop=TRUE) + 
  theme_few() + 
  theme(text = element_text(size=11, family="Times"))+
  labs(x="", y="") + 
  geom_linerange(aes(ymin=cil,ymax=cih))

disjunctionPlot_g <- ggplot_gtable(ggplot_build(disjunctionPlot))

strips <- grep("strip-r", disjunctionPlot_g$layout$name)

new_grobs <- list(cat, cat_dog)

disjunctionPlot_g <- with(disjunctionPlot_g$layout[strips,],
          gtable_add_grob(disjunctionPlot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

disjunctionPlot_g$widths[[8]] <- unit(2.5,"cm")

grid.draw(disjunctionPlot_g)
```

If detecting and reacting to underinformativity is the whole story, then disjunctive guesses should show similar degrees of infelicity, regardless of how many animals there are on the card. However, the results of the 3AFC task suggest otherwise. A logistic mixed-effects model with the random intercepts and slopes for subjects and fixed effect of disjunction type found that when comparing disjunctive guesses in the 3AFC task, participants were more likely to choose "kinda right" than "right" when both animals were on the card ($\beta$=`r round(disjunctTrialsModel$coefficients[2],2)`, $z$=`r round(disjunctTrialsModel$coefficients[6],2)`, $p$=`r round(disjunctTrialsModel$coefficients[8],2)`). In other words, participants judged further infelicity with disjunctive guesses that had both disjuncts as true. Therefore, it is possible that in some trials when both disjuncts were true, some participants went through the following pragmatic reasoning:

* **Reasoning on Alternatives**: Why did the guesser choose the under-informative connective *or* rather than the more informative *and*?

* **Resolution Assumption**: speaker is trying to be as specific as possible by resolving the issue of how many animals are on the card.

* **Exclusivity Implicature**: Given the resolution hypothesis, if the speaker had decided that two animals were on the card, they should have said *cat and dog*. They did not, so they had decided that only one animal is on the card and not both.

```{r rates}
adult_kindaWrong <- filter(prop_table, Guess=="Cat or Dog", Card=="XY", `Age Category`=="Adults", response=="Kinda Right")$prop[2]
  
adult_wrong  <- filter(prop_table, Guess=="Cat or Dog", Card=="XY", `Age Category`=="Adults", response=="Wrong")$prop[1]
```

How does the exclusivity implicature affect participant judgments in the experimental setting? One possibility is that excluding the correct response pragmatically is treated like cases of excluding the right response semantically. For example, guessing "elephant" when there is a cat on the card. The prediction is that disjunctive trials with true disjuncts should receive "wrong" responses. However, this prediction was not borne out. Such disjunctive trials are almost never judged as "wrong". 

Overall adults seem to differentiate incorrect pragmatics from incorrect semantics  (i.e. falsehood) and punish incorrect pragmatics less than incorrect semantics. This conclusion is supported by the response patterns across trial types (figure \@ref(fig:ternaryAdultsPlot)). Trial types that received a "wrong" response were those that were false. Pragmatically infelicitous trial types, namely simple guesses like *cat* or disjunctive guesses like *cat or dog* when both animals are on the card, receive "kinda right" responses. In other words, adults consider false utterances as "wrong" guesses but infelicitous utterances do not reach the level of being "wrong"; they are still right even though not completely right. This would explain why the rates of infelicity (avoiding the "right" alternative) differ between 2AFC and 3AFC tasks in disjunctive trials with true disjuncts (`r round(adult_wrong,2)`% vs. `r round(adult_kindaWrong,2)`%). 

```{r implicatureStats, eval=FALSE}
test <- glmer(response ~ Card + (1|sid), family = "binomial" , data = filter(data_main_dv2, Guess=="XorY"))
summary(test)

factor(filter(data_main_dv2, Guess=="XorY")$response)
```
-->
## Study 2: Children's three-alternative forcied choice judgments vs. open-ended verbal feedback{#study2}

```{r}
n_study2 <- length(unique(data_children$sid))

ageInfo_study2 <- c(floor(min(data_children$age_year)), 
                    round((min(data_children$age_year) - floor(min(data_children$age_year)))*12),
                    floor(max(data_children$age_year)),
                    round((max(data_children$age_year) - floor(max(data_children$age_year)))*12),
                    floor(mean(data_children$age_year)),
                    round((mean(data_children$age_year) - floor(mean(data_children$age_year)))*12)
                    )
```

The goal of this study was to examine children's interpretations of *and* and *or* in the guessing game and compare them to those of the adults'. Since the 3AFC judgment task in study 1 was better at capturing the nuances of adults' pragmatic reasoning, we decided to first test children using the 3AFC task. We also analyzed children's open-ended verbal feedback about the guesses in the same task. <!--Both 3AFC judgments and the analysis of children's open-ended feedback showed that children differentiate existential sentences with *and* from those with *or*. While the 3AFC task suggested that children consider disjunctive guesses with true disjuncts as felicitous, the analysis of their verbal feedback showed otherwise. Children took issue with such guesses and corrected them, often by mentioning the stronger alternative *and*. We conclude that the 3AFC task may have underestimated children's pragmatic competence.-->

### Methods

| Study | N | Age | Mode | Response Option |
|--------|--|-----------------|-------------|--------------------------|
| Study 2 | `r n_study2` | `r ageInfo_study2[1]`;`r ageInfo_study2[2]`-`r ageInfo_study2[3]`;`r ageInfo_study2[4]` (M = `r ageInfo_study2[5]`;`r ageInfo_study2[6]`) | Study Room | Circle (wrong), Little Star (little right), Big Star (right) |
Table: (\#tab:study2info) Summary of Study 2 Methods

<!--| Study 1 - Part 1 | `r n_adults2`| Adults | Online (Mturk) | Wrong, Right|
| Study 1 - Part 2 | `r n_adults3`| Adults | Online (Mturk) | Wrong, Kinda Right, Right|-->

#### Materials and Design

We used the same set of cards and linguistic stimuli as the ones in study 1. There were 8 trial types and 2 trials per trial type for a total of 16 trials. We made two changes to make the experiment more suitable for children. First, instead of the fictional character Bob, a puppet named Jazzy played the guessing game with them. Jazzy wore a sleeping mask over his eyes during the game (Figure \@ref(fig:jazzy)). Second, a pilot study showed that a scale with three alternatives is better understood and used by children if it is presented in the form of rewards to the puppet rather than verbal responses such as "wrong", "a little bit right", and "right", or even hand gestures such as thumbs up, middle, and down. Therefore, we placed a set of red circles, small blue stars, and big blue stars in front of the children. These tokens were used to reward the puppet after each guess. During the introduction, the experimenter explained that if the puppet is right, the child should give him a big star, if he is a little bit right, a little star, and if he is not right, a red circle. 

```{r jazzy, fig.width=2.5, fig.height=1.5, fig.env = 'figure', fig.cap="The puppet, Jazzy, with and without the sleeping mask."}
jazzy_img <- png::readPNG("figs/Jazzy.png")
grid::grid.raster(jazzy_img)
```

#### Participants and Procedure

We recruited `r n_study2` English speaking children from the Bing Nursery School at Stanford University. Children were between `r ageInfo_study2[1]`;`r ageInfo_study2[2]` and `r ageInfo_study2[3]`;`r ageInfo_study2[4]` years old (Mean = `r ageInfo_study2[5]`;`r ageInfo_study2[6]`). The experiment was carried out in a quiet room and all sessions were videotaped. There was a small table and two chairs in the room. Children sat on one side of the table and the experimenter and the puppet on the other side facing the child. The groups of circles, small stars, and big stars were placed in front of the child from left to right. A deck of six cards was in front of the experimenter. As in study 1 with adults, the children went through three phases: introduction, instruction, and test. 

The goal of the introduction was for the experimenter to show the cards to the children and make sure they recognized the animals and knew their names. The experimenter showed the cards to the children and asked them to label each animal. All children recognized the animals and could label them correctly. In the instruction phase, children went through three example trials. The experimenter explained that he was going to play with the puppet first, so that the child could learn the game. He removed the six introduction cards and placed a deck of three cards face-down on the table. From top to bottom (first to last), the cards had the following images: cat, elephant, cat and dog (Table \@ref(tab:instruction)). He put the sleeping mask on the puppet's eyes and explained that the puppet is going to guess what animal is on the cards. He then picked the first card and asked the puppet: "What do you think is on this card?" The puppet replied with "There is a dog". The experimenter showed the cat-card to the child and explained that when the puppet is "not right" he gets a circle. The pilot study had shown that some children struggle with understanding the word "wrong", so "not right" was used instead. He then asked the child to give the puppet a circle. Rewards were collected by the experimenter and placed under the table to not distract the child. The second trial followed the same pattern except that the puppet guessed "right" and the experimenter invited the child to give the puppet a big star. In the final trial, the puppet guessed that there is a cat on the card when the card had a cat and a dog on it. The experimenter said that the puppet was "a little right" and asked the child to give him a little star.

|Card | Guess | Reward |
|-----|-----|-----|
|CAT | There is a dog! | Circle |
|ELEPHANT | There is an elephant!| Big Star | 
|CAT-DOG | There is a dog! | Little Star |
Table: (\#tab:instruction) Instruction Trials.

In the test phase, the experimenter removed the three instruction cards and placed a deck of 16 randomized cards on the table. He explained that it was the child's turn to play with the puppet. For each card, the puppet provided a guess and the child provided the puppet with a reward.

#### Offline Annotations {#feedbackCoding}

While playing the game, children often provided spontaneous verbal reactions to the puppet's guesses. During the analysis of the videos, these verbal responses were categorized into four types: 1. None, 2. Judgments, 3. Descriptions, and 4. Corrections. The first category referred to cases where children did not say anything and only rewarded the puppet. Judgments referred to linguistic feedback such as "you are right!", "yes", "nope", or "you winned". Such feedback only expressed judgments and complemented the rewards. Descriptions were cases that the child simply mentioned what was on the card: "cat!", "dog and elephant!", "There is a cat and a dog!" etc. Finally, corrections referred to feedback that provided "focus words" (e.g. *just*, *only*, *AND*) that acted like corrections to what the puppet had said. Examples include: "Just a cat!", "Both!", "The two are!", "Only cat!", "cat AND dog" (with emphasis placed on *and*). In trials where the child provided both judgments as well as descriptions or corrections (e.g. "Yes! Cat!"), we placed the feedback into the more informative categories, namely description or correction.

### Results 

```{r childrenTernaryPlot, fig.env = "figure", fig.cap = "Children's 3AFC judgments in the connective guessing game."}
prop_table$response <- fct_recode(prop_table$response, `A Little Right`="Kinda Right")

child_plot_tvjt <-
  prop_table %>%
  filter(`Age Category`=="Children") %>%
  ggplot(aes(x=response, y=prop, fill=response)) + 
  geom_bar(stat="identity", width=0.6) + 
  facet_grid(Card~Guess) +
  geom_linerange(aes(ymin=cil, ymax=cih)) +
  labs(x="",y="") +
  theme_few() +
  theme(axis.text.x = element_text(angle=45, hjust=1, vjust=1), text = element_text(size=11, family="Times")) + 
  scale_fill_manual(values = c("red4", "grey","springgreen3"), guide=FALSE)

child_plot_tvjt_g <- ggplot_gtable(ggplot_build(child_plot_tvjt))

strips <- grep("strip-r", child_plot_tvjt_g$layout$name)

new_grobs <- list(cat, cat_dog)

child_plot_tvjt_g <- with(child_plot_tvjt_g$layout[strips,],
          gtable_add_grob(child_plot_tvjt_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

child_plot_tvjt_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(child_plot_tvjt_g)
```

Figure \@ref(fig:childrenTernaryPlot) shows the results for children's 3AFC judgments. Starting from the left column, if the mentioned animal was not on the card (e.g. elephant), children judged the guess as "wrong". If the animal mentioned (e.g. cat) was the only animal on the card, children judged the guess to be "right". Here we ignore the results for trial types in which the animal mentioned was one of the animals on the card. The reason is that such trials were used in the instruction phase to introduce the "little bit right" option, and the results are probably biased by the instructions.

In conjunctive guesses (e.g. *cat and dog*), when only one of the animals mentioned was on the card, children judged the guess as "wrong" or "a little bit right". However, if both animals were on the card, they judged it "right". In disjunctive guesses (e.g. *cat or dog*), when only one of the animals mentioned was on the card, children considered the guess "right" or "kinda right". If both animals were on the card, it was considered "right".
<!--
The comparison of conjunction and disjunction trials (last two columns of figure \@ref(fig:childrenTernaryPlot)) shows that overall, children distinguished between *and* and *or* when one animal was on the card. Given that the one-animal conjunction trials are false but the one-animal disjunction trials are true, the difference in response patterns may suggest that children understood the truth-conditional differences between *and* and *or*. The truth judgments did not provide evidence that children differentiated *and* and *or* when two animals were on the card. Since in the majority of examples with *or* and two animals, children responded with "right", it is possible to conclude from the 3AFC judgment data that children did not generate exclusivity inferences in this task.
-->
Figure \@ref(fig:childAdultComp) compares the results for children and adults' 3AFC judgments in the conjunction and disjunction trials. The major difference between adults and children's responses was disjunctive trials with two animals on the card. Most children considered such trials as "right" while most adults considered them as "kinda right". In the next section, we use Bayesian regression modeling to compare adults' and children's three-alternative responses more systematically. 

```{r childAdultComp, fig.env = "figure", fig.cap = "Comparison of Adults' and Children's 3AFC judgments."}
child_adult_comp <-
  prop_table %>%
  filter(Options==3, Guess!="Elephant", Guess!="Cat") %>%
  ggplot(aes(x=response, y=prop, fill=`Age Category`)) + 
  geom_bar(stat="identity", width=0.6, position = "dodge") + 
  facet_grid(Card~Guess) +
  geom_linerange(aes(ymin=cil, ymax=cih), position = position_dodge(width=0.6)) +
  labs(x="",y="") +
  theme_few() +
  theme(axis.text.x = element_text(angle=45, hjust=1, vjust=1), text = element_text(size=11, family="Times")) + 
  scale_fill_manual(values = c("grey", "red4"))

child_adult_comp_g <- ggplot_gtable(ggplot_build(child_adult_comp))

strips <- grep("strip-r", child_adult_comp_g$layout$name)

new_grobs <- list(cat, cat_dog)

child_adult_comp_g <- with(child_adult_comp_g$layout[strips,],
          gtable_add_grob(child_adult_comp_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

child_adult_comp_g$widths[[8]] <- unit(2.5,"cm")

grid.draw(child_adult_comp_g)
```

#### Analysis and Statistical Modeling

```{r rstanModel}
adult_samples <- read_csv("study2/3_analysis/adult_samples")
child_samples <- read_csv("study2/3_analysis/child_samples")

adult_comps <- filter(adult_samples, 
                 Parameter %in% c("alpha","beta_x_or",
                                  "beta_x_and","beta_xy_or"))

child_comps <- filter(child_samples, 
                 Parameter %in% c("alpha","beta_x_or",
                                  "beta_x_and","beta_xy_or"))

acomp_tab <- adult_comps %>%
  spread(Parameter, value) %>%
  mutate(`b(AND,2)-b(AND,1)` = alpha - beta_x_and,
         `b(OR,1)-b(AND,1)` = beta_x_or - beta_x_and, 
         `b(OR,2)-b(OR,1)` = beta_xy_or - beta_x_or) %>%
  select(-alpha, -beta_x_and, -beta_x_or) %>%
  rename(`b(OR,2)`=beta_xy_or) %>%
  gather(Parameter, value, `b(AND,2)-b(AND,1)`, `b(OR,1)-b(AND,1)`, 
         `b(OR,2)-b(OR,1)`, `b(OR,2)`) %>%
  group_by(Parameter) %>%
  summarise(mean = mean(value), 
            hdp_lower = quantile(value, .01),
            hdp_upper = quantile(value, .99)) 

ccomp_tab <- child_comps %>%
  spread(Parameter, value) %>%
  mutate(`b(AND,2)-b(AND,1)` = alpha - beta_x_and,
         `b(OR,1)-b(AND,1)` =  beta_x_or - beta_x_and, 
         `b(OR,2)-b(OR,1)` = beta_xy_or - beta_x_or) %>%
  select(-alpha, -beta_x_and, -beta_x_or) %>%
  rename(`b(OR,2)`=beta_xy_or) %>%
  gather(Parameter, value, `b(AND,2)-b(AND,1)`, `b(OR,1)-b(AND,1)`, 
         `b(OR,2)-b(OR,1)`, `b(OR,2)`) %>%
  group_by(Parameter) %>%
  summarise(mean = mean(value), 
            hdp_lower = quantile(value, .01),
            hdp_upper = quantile(value, .99)) 

ccomp_tab[,"Age"] <- "child"
acomp_tab[,"Age"] <- "adult"
comp_tabs <- rbind(ccomp_tab, acomp_tab)
comp_tabs$Age <- factor(comp_tabs$Age)
```

```{r stanModelPlot, fig.env="figure", fig.width=4.5, fig.pos = "!h", fig.height=2.5, fig.cap = "Coefficients capturing the relevant comparisons across conditions in 3AFC judgments in Study 1 and 2. In naming the coefficients like b(OR,2), OR/AND represents the connective used and the number 1/2 represents the number of animals on the card. Error bars represent 99\\% regions of highest posterior density."}

ggplot(comp_tabs, aes(y=mean,x=Parameter, color=Age)) + 
  geom_point(position = position_dodge(width = .1)) + 
  geom_hline(yintercept=0, linetype="dashed") + 
  geom_linerange(aes(ymin=hdp_lower, ymax=hdp_upper), 
                 position = position_dodge(width = .1)) + 
  labs(y="Difference in Parameter Means", x="Trial Type Contrasts") + 
  scale_colour_solarized() + 
  theme(text = element_text(size=11, family="Times")) +
  theme_few() + 
  coord_flip()
```

We used the R package RStan for Bayesian statistical modeling to fit separate ordinal mixed-effects logistic models for adults' and children's judgments. The response variable had three ordered levels: *wrong*, *kinda right*, and *right*. The trial types *One-Animal-OR*, *Two-Animals-OR*, *One-Animal-AND* constituted the (dummy-coded) fixed effects of the model with *Two-Animals-AND* set as the intercept. The model also included by-subject random intercepts. The priors over trial types and the random intercepts were set to $\mathcal{N}(0,10)$. We also included parameters $C_1$ and $C_2$, the two cutpoints delimiting the logistic for 1) *wrong* and *kinda right* and 2) *kinda right* and *right* responses, drawn with the prior $\mathcal{N}(0,1)$.^[We used a tight prior in this case to decrease posterior correlations between cutpoints and intercept.] All four chains converged after 3000 samples (with a burn-in period of 1500 samples).

We made inferences based on the highest-posterior density (HPD) intervals for the coefficients estimated from each model. Because predictors are dummy-coded, it's possible to examine contrasts of interest by computing the difference between coefficients for pairs of conditions we wish to contrast. In naming the coefficients like b(OR,2), OR/AND represents the connective used and the number represents the number of animals on the card. Figure \@ref(fig:stanModelPlot) shows the contrasts of interest: *b(OR, 2)-b(OR,1)*  represents the difference between the estimated coefficients for the disjunction trials with two animal on the card and those with only one; *b(OR, 2)* represents the difference between the estimated coefficients for the conjunction trials with two animals and the disjunction trials with two animals; and so on.

Overall, adults' and children's estimated coefficients are similar in sign to one another, though adults' are more extreme. In the conjunction trials (*b(AND, 2)-b(AND,1)*), children and adults showed a strong preference for the cards with two animals rather than one. At the same time, given two animals on the card, children and adults showed a preference for *and* rather than *or* (*b(OR, 2)*). However, with only one animal on the card, children and adults preferred a disjunctive guess (*b(OR, 1)-b(AND,1)*). These results are compatible with the truth conditions of conjunction and disjunction.

The main difference between adults and children shows up in the contrast between the disjunctive trial types: two animals vs. only one (*b(OR, 2)-b(OR,1)*). On average, children rated disjunction trials with two animals higher than those with only one. Adults on the other hand showed the opposite pattern: they rated disjunction trials with two animals lower. This pattern is compatible with current accounts of pragmatic development that suggest children's interpretations tend to be more literal than adults [@noveck2001children; @papafragou2003scalar; @barner2011accessing].

The slight preference children show for cards with two animals when the guess is disjunctive (e.g. "cat or dog") is also compatible with the account proposed by @Singh2016 and @tieu2016. However, the effect seems much smaller here than was reported in their studies. The comparison with conjunction trials makes it clear that overall, children are not interpreting *or* as a conjunction. The effect in this study can be more accurately described as a preference in truth value judgments for both disjuncts being true rather than a conjunctive interpretation of disjunction. The results from children's spontaneous linguistic feedback provide more evidence that children are not interpreting *or* as a conjunction. We will discuss these results next.

#### Children's open-ended feedback

```{r chisq-tests}
criticals <- 
  data_main_dv3 %>% filter(!is.na(response),  age_category== "Children", 
         trial_type %in% c("X.XorY","X.XandY","XY.XorY","XY.XandY"))
criticals$trial_type <- factor(criticals$trial_type)

ctable <-
  criticals %>% select(feedback, trial_type) %>%
  group_by(trial_type, feedback) %>%
  summarise (counts = n()) %>%
  spread(trial_type, counts)
ctable <- as.data.frame(ctable)

chisq_1andor <- chisq.test(ctable[,2], p= ctable[,3], rescale.p = T)
chisq_and12 <- chisq.test(ctable[,2], p = ctable[,4], rescale.p = T)
chisq_1and2or <- chisq.test(ctable[,2], p = ctable[,5], rescale.p = T)
chisq_1or2and <- chisq.test(ctable[,3], p= ctable[,4], rescale.p = T)
chisq_or12 <- chisq.test(ctable[,"X.XorY"], 
                         ctable[,"XY.XorY"], 
                         rescale.p = TRUE)
chisq_2andor <- chisq.test(ctable[,"XY.XandY"], 
                           p=ctable[, "XY.XorY"], rescale.p = T)

```

|Category | Definition | Examples |
|-----------|-----------------------------------|------------------------|
|**None** | no verbal feedback | | 
|**Judgment** | provided verbal judgment mirroring the reward | "No!", "Yes!" , "You are right!" | 
|**Description** | mentioned the animal(s) on the card | "elephant", "cat and dog" |
|**Correction** | used focus particles like *only*/*just*, emphasized *and* or used *both* | "only cat", "just elephant", "both!", "cat AND dog!"|

Table: (\#tab:feedbackCat) Definitions and Examples for the Feedback Categories.

As explained in section \@ref(feedbackCoding), we also categorized and annotated children's spontaneous and free-form verbal reactions to the puppet's guesses. Table \@ref(tab:feedbackCat) summarizes the definitions and examples for each category and Figure \@ref(fig:feedbackData) shows the results. We should point out that each trial type had a similar number of "None" cases. Some children remained more or less silent throughout the experiment and only provided rewards to the puppet. In the next study we ask children to provide feedback explicitly and therefore we have no "None" responses. In the discussion and analysis here we will not comment further on the "None" category but focus on the other three categories.

```{r feedbackData, fig.env="figure", fig.cap = "Children's open-ended Feedback. Error bars represent 95\\% confidence intervals." }

study2_feedback <-
  data_children %>%
  group_by(sid, trial_type, feedback) %>%
  summarise(counts= n()) %>%
  spread(feedback, counts) %>%
  replace(is.na(.), 0) %>%
  mutate(total = None + Judgement + Description + Correction) %>%
  gather(feedback, counts, Correction:None) %>%
  mutate(prop = counts / total) %>%
  group_by(trial_type, feedback) %>%
  summarize(cih = ci.high(prop),
            cil = ci.low(prop),
            prop = mean(prop)) %>%
  separate(trial_type, into = c("animal", "connective"), sep="\\.")

study2_feedback$feedback <- factor(study2_feedback$feedback, levels = c("None", "Judgement", "Description", "Correction"))

study2_feedback$connective <- 
  study2_feedback$connective %>%
  factor() %>%
  fct_relevel("Z") %>%
  fct_recode(Cat = "X", Elephant = "Z", `Cat or Dog`="XorY", `Cat and Dog`="XandY")
  
study2_feedbackPlot <-
  ggplot(study2_feedback, 
       aes(x=feedback, y=prop, fill=feedback)) + 
  geom_bar(stat="identity", width = 0.6, position="dodge") + 
  geom_linerange(aes(ymax = cih, ymin = cil)) + 
  facet_grid(animal~connective) + 
  labs(title = "", x = "", y = "") + 
  theme_few() + 
  theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = .5), text = element_text(size=11, family="Times")) + 
#  scale_fill_solarized(guide=FALSE)
  scale_fill_manual(values = c("gray", "red2", "red3", "red4"), guide=FALSE)

study2_feedbackPlot_g <- ggplot_gtable(ggplot_build(study2_feedbackPlot))

strips <- grep("strip-r", study2_feedbackPlot_g$layout$name)

cat <- readJPEG("study1/0_methods/stimuli/cat_card.jpg") %>% rasterGrob(width=0.9)

cat_dog <- readJPEG("study1/0_methods/stimuli/catdog_card.jpg")%>% rasterGrob(width=0.9)

new_grobs <- list(cat, cat_dog)

study2_feedbackPlot_g <- with(study2_feedbackPlot_g$layout[strips,],
          gtable_add_grob(study2_feedbackPlot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

study2_feedbackPlot_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(study2_feedbackPlot_g)
```

In the leftmost column, when the guessed animal was not on the card (e.g. "there is an elephant"), children either provided judgments like "No!" or described what was on the card (e.g. "cat" or "cat and dog"). However, when the guessed animal was the only animal on the card (e.g. "there is a cat"), most children provided a positive judgment like "Yes". When the animal guessed was only one of the animals on the card, children described what was on the card (e.g. cat and dog).

In the critical trial types with conjunction and disjunction, children showed a high rate of corrections and descriptions when there was only one animal on the card (e.g. cat) and the guess was a conjunction (e.g. "there is a cat and a dog"). In their corrections, children used the focus particles *just* and *only* as in "just a cat" or "only a cat". However, when both animals were on the card and a conjunction was used (e.g. "there is a cat and a dog"), children predominantly provided positive judgments like "Yes!" and "You are right". Considering disjunctive guesses like "cat or dog", when only one of the animals was on the card, most children simply described what was on the card (e.g. "cat"). However, when both animals were on the card, children corrected the puppet by saying "Both!" or emphasizing *and* as in "cat AND dog!".

We performed chi-squared goodness-of-fit tests to compare the feedback distributions in the critical conditions with *and* and *or*. Here we focus on those trials (the four bar charts on the right of Figure \@ref(fig:feedbackData)). Children's linguistic feedback showed three patterns. First, the one-animal conjunctive and two-animal disjunctive (top left and bottom right) trials contained a higher proportion of corrections than the other trial types. These were trials where the guesses were either false or infelicitous. In the conjunction trials, a comparison of the feedback distribution in one-animal and two-animal conditions was statistically significant ($\chi^2$(`r chisq_and12$parameter`, `r sum(chisq_and12$observed)`) = `r  round(chisq_and12$statistic,2)`, p < .0001), suggesting that children gave different feedback to true and false guesses. A similar numerical trend was present in the disjunction trials, but it was not significant ($\chi^2$(`r chisq_or12$parameter`, `r sum(chisq_or12$observed)`) = `r round(chisq_or12$statistic,2)`, p = `r round(chisq_or12$p.value,2)`). 

Second, the one-animal disjunctive trials (top right) showed the highest proportion of "descriptions". These are trials in which the guess is correct but not specific enough: it leaves two possibilities open. These trials were significantly different from the one-animal trials for conjunction ($\chi^2$(`r chisq_1andor$parameter`, `r sum(chisq_1andor$observed)`) = `r round(chisq_1andor$statistic,2)`, p < .0001). Finally, the two-animal conjunctive trials (bottom left) showed the highest proportion of "judgments" such as *You are right!*. This was not surprising given that these trials represented the optimal guessing scenario. These trials had a significantly different feedback distribution from the matching disjunction trials ($\chi^2$(`r chisq_2andor$parameter`, `r sum(chisq_2andor$observed)`) = `r round(chisq_2andor$statistic,2)`, p < .0001).

### Discussion

In study 2, we used a 3AFC judgment task to test children's comprehension of logical connectives *and* and *or*. We compared these results to those found in the 3AFC judgment task of study 1 with adults. The general comparison showed that adults and children had similar patterns of judgments, except when both disjuncts were true. In such cases, adults judged the disjunctive guess as not completely right while most children judged it as completely right. There was even a slight preference among children to rewarded the puppet more in such cases, compared to cases of disjunction when only one disjunct was true.

To consider another measure of children's comprehension, we also looked at children’s spontaneous open-ended verbal feedback to the puppet's guesses. Our analyses suggested that children recognized false and infelicitous utterances with the connectives and provided appropriate corrective feedback. As expected from an adult-like understanding of connectives, children corrected the puppet most often when there was only one animal on the card and the guess was conjunctive, or when there were two animals on the card and the guess was disjunctive. Perhaps the most important finding was that children increased their corrective feedback in disjunctive guesses where both disjuncts were true, compared to those with only one true disjunct. These findings differ from the results of the 3AFC judgment task which suggested that children did not find any infelicity with disjunctive guesses when both disjuncts were true.

The analysis of children's open-ended feedback raises two important issues. First, it runs counter to what the 3AFC judgment task suggests with respect to exclusivity implicatures. The forced-choice task suggests that children find such underinformative utterances as unproblematic while analysis of their spontaneous feedback shows that they provided more corrections to such utterances. Second, one of the explanations for why children fail to derive implicatures is that they cannot access the stronger alternative to the disjunction word *or*, namely *and* [@barner2011accessing]. However, in the context of the guessing game, some children explicitly mentioned the word *and*, as the word the puppet should have said instead of *or*. Interestingly, these children continued to reward the puppet and considered the guess "right", even though they corrected him. This raises the possibility that forced-choice truth value judgments underestimate children's pragmatic knowledge. In study 3, we used both a 2AFC truth judgment task and an analysis of children's open-ended feedback. If the findings of study 2 were on the right track, we expected to replicate the same pattern in study 3, and find that children's open-ended feedback better reflects their sensitivity to pragmatic violations than the results of the 2AFC judgments.

## Study 3: Children's 2AFC judgments and open-ended feedback{#study3}

```{r study3Wrangling}
# load data for study 3
data_study3 <- read.csv("study3/2_processed_data/study2_data")

# exclusions: those trials with both Yes AND No responses, and those trials that had no response
tvjt_exclusion <-
  data_study3 %>%
  filter(tvjt=="YN" | is.na(tvjt))

# exclusions: trials with no feedback 
feedback_exclusion <-
  data_study3 %>%
  filter(feedback=="0")

data_study3$Guess <- 
  data_study3$Guess %>%
  factor(levels = c("Z", "X", "XandY", "XorY")) %>%
  fct_recode(Elephant = "Z", Cat = "X", `Cat and Dog`="XandY", `Cat or Dog`="XorY")

data_study3$tvjt <- 
  data_study3$tvjt %>%
  factor(levels = c("N", "Y")) %>%
  fct_recode(Yes = "Y", No = "N")

n_study3 <- length(unique(data_study3$id))

ageInfo_study3 <- c(floor(min(data_study3$age*0.00273973)), # Min age in year
                    round((min(data_study3$age*0.00273973)-floor(min(data_study3$age*0.00273973)))*12), #Min age months
                    floor(max(data_study3$age*0.00273973)), # Max age year
                    round((max(data_study3$age*0.00273973)-floor(max(data_study3$age*0.00273973)))*12), # Max age months
                    floor(mean(data_study3$age*0.00273973)), # Mean age year
                    round((mean(data_study3$age*0.00273973)-floor(mean(data_study3$age*0.00273973)))*12)) # Mean age months
```

This study used the same paradigm as study 2 but focused on children's open-ended feedback and aimed at replicating the findings in study 2. The main hypothesis was that four-year-olds provide corrective feedback to the puppet if both disjuncts are true, but they do not consider this infelicity to be grave enough to render the guess itself "wrong" in a 2AFC judgment task. The main hypothesis along with relevant analyses and predictions were preregistered in an "As Predicted" format[^9].

[^9]: The As Predicted PDF document is accessible at https://aspredicted.org/x9ez2.pdf.

### Methods

|Study | N | Age | Mode | Response Options |
|---------------|-|----------------|--------|--------------------------|
|Study 3 | `r n_study3` | `r ageInfo_study3[1]`;`r ageInfo_study3[2]`-`r ageInfo_study3[3]`;`r ageInfo_study3[4]` (M = `r ageInfo_study3[5]`;`r ageInfo_study3[6]`) | Study Room | Yes (Right)/No (Wrong) - Open-ended Feedback |
Table: (\#tab:study3info) Summary of Study 3 Methods

<!--
|Study 1 - Part 1 | `r n_adults2`| Adults | Online (Mturk) | Wrong, Right|
|Study 1 - Part 2 | `r n_adults3`| Adults | Online (Mturk) | Wrong, Kinda Right, Right|
|Study 2 | `r n_study2` | `r ageInfo_study2[1]`;`r ageInfo_study2[2]`-`r ageInfo_study2[3]`;`r ageInfo_study2[4]` (M = `r ageInfo_study2[5]`;`r ageInfo_study2[6]`) | Study Room | Circle (Wrong), Little Star (Little Right), Big Star (Right) |-->

#### Materials and Design

Study 3 was similar to Study 2 but differed in how children provided their judgments. Based on the findings in Study 2, we focused on verbal feedback, instead of rewards. We used two different ways of measuring children's judgments. First, we encouraged children to provide verbal feedback to the puppet. They were asked to say "yes" when the puppet was right, "no" when he was not, and then help him say it better. After children were done with this initial open-ended feedback, for each trial we asked a forced choice yes/no judgment question: "Was Jazzy (the puppet) right?". This question elicited a 2AFC response for each trial independent of children's earlier open-ended response. These two measures allowed us to compare open-ended and binary forced-choice judgments in the same setup.

#### Participants and Procedure

We recruited `r n_study3` English speaking children from the Bing Nursery School at Stanford University. Children were between `r ageInfo_study3[1]`;`r ageInfo_study3[2]` and `r ageInfo_study3[3]`;`r ageInfo_study3[4]` years old (Mean = `r ageInfo_study3[5]`;`r ageInfo_study3[6]`). The setup and procedure were similar to Study 2, except there were no rewards on the table. As before, participants sat through three phases: introduction, instruction, and test. The introduction phase made sure children knew the names of the animals on the cards. In the instruction phase, they received four training trials, as shown in Table \@ref(tab:instructionStudy3).

As in Study 2, the experimenter put a sleeping mask over the puppet's eyes and explained that Jazzy (the puppet) was going to guess what animal was on the cards. He then picked the first card and asked the puppet: "What do you think is on this card?" The puppet replied with "There is a dog". The experimenter showed the cat-card to the child and said: when Jazzy is "not right", tell him "no". He then asked the child to say "no" to the puppet. The second trial followed the same pattern except that the puppet guessed "right" and the experimenter invited the child to say "yes" to the puppet. There were two more instruction trials before the test phase began. The test phase contained 16 randomized trials, half of which contained guesses with the words *and* and *or*. The randomization code as well as the details of the methods are available on this paper's online repository.

|Card | Guess | Response |
|------|---------------|------|
|CAT | there is a dog! | No! |
|ELEPHANT | there is an elephant!| Yes! | 
|DOG-ELEPHANT | there is a cat! | No! |
|DOG | there is a dog! | Yes! |
Table: (\#tab:instructionStudy3) Instruction Trials for Study 3.

### Results

```{r study3JudgementTable}
study3_tvjt <-
  data_study3 %>%
  filter(tvjt!="YN", !is.na(tvjt)) %>% #exclusion
  group_by(id, Animal, critical, Guess, tvjt) %>%
  summarise(counts= n()) %>%
  spread(tvjt, counts) %>%
  replace(is.na(.), 0) %>%
  mutate(total = No + Yes) %>%
  gather(tvjt, counts, No:Yes) %>%
  mutate(prop = counts / total) %>%
  group_by(Animal, Guess, tvjt, critical) %>%
  summarize(cih = ci.high(prop),
            cil = ci.low(prop),
            prop = mean(prop))
```

We first look at the results of the 2AFC judgement task for each trial type and compare them to those of the adults' in Study 1. Then we analyze children's open-ended responses and compare them to the forced choice responses obtained in the same trial types. For the 2AFC judgments we excluded `r nrow(tvjt_exclusion)` trials (out of total `r nrow(data_study3)`) where children either did not provide a Yes/No response or provided both (i.e. "Yes and No"). The exclusions were almost equally distributed among different types of guesses and cards. In the analysis of children's open-ended feedback, we excluded `r nrow(feedback_exclusion)` trials (out of total `r nrow(data_study3)`) where children either did not provide any feedback or their feedback could not be categorized into the existing categories.

#### Two-Alternative Forced Choice Judgments

```{r Study3tvjtPlot, fig.cap = "Children's binary truth value judgments."}
tvjt_plot <-
  study3_tvjt %>%
  ggplot(aes(x=tvjt, y=prop, fill=tvjt)) + 
  geom_bar(stat="identity", width = 0.6, position="dodge") + 
  geom_linerange(aes(ymax = cih, ymin = cil)) + 
  facet_grid(Animal~Guess) + 
  guides(fill=FALSE) + 
  labs(title = "", x = "", y = "") + 
  theme_few() + 
  theme(text = element_text(size=11, family="Times")) + 
  scale_fill_manual(values = c("red3", "springgreen3"))

tvjt_plot_g <- ggplot_gtable(ggplot_build(tvjt_plot))

strips <- grep("strip-r", tvjt_plot_g$layout$name)

new_grobs <- list(cat, cat_dog)

tvjt_plot_g <- with(tvjt_plot_g$layout[strips,],
          gtable_add_grob(tvjt_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

tvjt_plot_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(tvjt_plot_g)
```

```{r binaryStats}
data_study3$Guess <- 
  data_study3$Guess %>%
  fct_recode(Z= "Elephant", X = "Cat", XandY = "Cat and Dog", XorY = "Cat or Dog")

binaryStats_children <-
  data_study3 %>%
  filter(tvjt!="YN", !is.na(tvjt)) %>%
  select(Animal, Guess, tvjt, id) %>%
  rename(response="tvjt", sid="id", Card = "Animal")

binaryStats_children[,"age_category"] <- "Children"

binaryStats_children$response <- recode(binaryStats_children$response, Yes="Right", No="Wrong") # change yes no to right and wrong

binaryStats_adults <-
  filter(data_adults, dv_type==2) %>%
  select(sid, response, age_category, Card, Guess)

binaryStats <- bind_rows(binaryStats_adults, binaryStats_children)
binaryStats$response <- factor(binaryStats$response, levels=c("Wrong", "Right"))

oneDisjunct_model <- summary(glmer(response ~ age_category + (1|sid), family= "binomial", data=filter(binaryStats, Card=="X", Guess=="XorY")))

twoDisjunct_model <- summary(glmer(response ~ age_category + (1|sid), family= "binomial", data=filter(binaryStats, Card=="X", Guess=="XandY")))

childDisj_model <- summary(glmer(response ~ Card + (1|sid), family= "binomial", data=filter(binaryStats, age_category=="Children", Guess=="XorY")))

#critical_binaryStats <- filter(binaryStats, Guess=="XandY" | Guess=="XorY")

#overall_model <- summary(brm(response ~ Card * Guess * age_category + (1|sid), family= binomial(link=logit), data=critical_binaryStats))
```

Figure \@ref(fig:Study3tvjtPlot) shows children's 2AFC judgments. In the leftmost column, when the animal guessed was not on the card  (e.g. elephant), children considered the guess "wrong". When the animal guessed was the only animal on the card (e.g. cat), children considered the guess "right". However, if the animal guessed (e.g. cat) was only one of the animals on the card, children were equally split between "wrong" and "right" judgments. On the other hand, almost all adults considered such guesses "right" in their 2AFC judgments (Figure \@ref(fig:binaryAdultsPlot)). In such trial types, children seem to interpret the guess "there is a cat" as "there is **only** a cat", while adults do not. This difference between children and adults is unexpected for a theory of meaning acquisition that assumes children are overall more logical or literal as interpreters than adults [@noveck2001children].

In the trials with *and* and *or*, children's judgments were similar to those of adults. Figure \@ref(fig:BinaryPlotComp) compares adults' and children's 2AFC judgments. In trials with conjunction, when only one of the animals was on the card, most children considered the guess "wrong". This is similar to adults' judgments, but different in extent: adults were more consistent and unanimous in rejecting such guesses. A mixed effects logistic regression with the fixed effect of age category (adult vs. child) and random effect of subject found no significant difference between adults' and children's responses in such trials (see Table \@ref(tab:statsStudy3), Conjunction - One Animal). 

|Trial Data | Coefficient | Standard Error | Z-Value | P-value |
|---------|:-------:|:-------:|:------:|:-------:|
|Conjunction - One Animal | `r round(oneDisjunct_model$coefficients[2],2)` | `r round(oneDisjunct_model$coefficients[4],2)` | `r round(oneDisjunct_model$coefficients[6],2)` | `r round(oneDisjunct_model$coefficients[8],2)` |
|Disjunction - One Animal | `r round(twoDisjunct_model$coefficients[2],2)` | `r round(twoDisjunct_model$coefficients[4],2)` | `r round(twoDisjunct_model$coefficients[6],2)` | `r round(twoDisjunct_model$coefficients[8],2)` |

Table: (\#tab:statsStudy3) Mixed effects logistic models for conjunction and disjunction trials when only one disjunct was true, in 2AFC judgments of adults and children, using `glmer` in R's lme4 package. Formula: $Response \sim Age Category + (1|Subject)$.

In conjunctive guesses where both animals were on the card, both children and adults were unanimous in considering the guess "right". In disjunctive trials when only one of the animals was on the card, most children considered the guess "right". This is again similar to adults but differs from them in extent: adults more consistently and unanimously judged such guesses as "right". Yet again, a mixed effects logistic regression with the fixed effect of age (adult vs. child) and random effect of subject found no significant difference between adults' and children's responses in such trials (see Table \@ref(tab:statsStudy3), Disjunction - One Animal). Adults and children showed almost identical patterns of judgments in trials where there was two animals on the card and the guess used the connective *or*. Children and adults did not differ in their rate of rejecting disjunctive guesses when both disjuncts were true.

```{r BinaryPlotComp, fig.env="figure", fig.cap="The comparison of the 2AFC judgment task for conjunction and disjunction trials in adults (study 1) and children (study 3)."}

child_binary <-
  study3_tvjt %>% 
  rename(Card="Animal", response="tvjt") %>%
  select(-critical) %>%
  filter(Guess!="Elephant", Guess!="Cat")

child_binary[,"Age Category"] <- "Children" # add age category 
child_binary$response <- recode(child_binary$response, Yes="Right", No="Wrong") # change yes no to right and wrong

adult_binary <-
  prop_table %>%
  filter(Options==2, response!="Kinda Right", `Age Category`=="Adults", Guess!="Cat", Guess!="Elephant") %>% ungroup() %>% select(-Options)

adult_binary$response <- fct_drop(adult_binary$response)

binary_comp <-
  bind_rows(adult_binary, child_binary)

binary_comp$response <- fct_relevel(binary_comp$response, "Wrong")

binary_compPlot <-
  binary_comp %>%
  filter(response!="A Little Right") %>%
  ggplot(aes(x=response, y=prop, fill=`Age Category`)) + 
  geom_bar(stat = "identity", position = "dodge", width=0.6) + 
  geom_linerange(aes(ymin=cil,ymax=cih), position = position_dodge(width=0.6)) +
  facet_grid(Card~Guess) + 
  labs(x="",y="") +
  theme_few() +
  theme(text = element_text(size=11, family="Times")) + 
  scale_fill_manual(values = c("grey", "red4"))

binary_compPlot_g <- ggplot_gtable(ggplot_build(binary_compPlot))

strips <- grep("strip-r", binary_compPlot_g$layout$name)

new_grobs <- list(cat, cat_dog)

binary_compPlot_g <- with(binary_compPlot_g$layout[strips,],
          gtable_add_grob(binary_compPlot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

binary_compPlot_g$widths[[8]] <- unit(2.5,"cm")

grid.draw(binary_compPlot_g)
```

Finally, there is a small but significant preference in children's judgments of disjunctive statements for both disjuncts to be true. Comparing the disjunctive trials with one animal and two animals on the card, a mixed-effects logistic model with the fixed effect of disjunction type and the random effect of subjects found that children had a slight preference for both animals to be on the card ($b$= `r round(childDisj_model$coefficients[2],2)`, $se$= `r round(childDisj_model$coefficients[4],2)`, $z$= `r round(childDisj_model$coefficients[6],2)`, $p < 0.001$ ). There was a similar small trend in children's three-alternative judgments in study 2. While this was quite small compared to the other effects observed in these studies, it nevertheless indicated a difference between children's and adults' truth judgments. We return to this in more detail in section \@ref(conjunctive) of the General Discussion.

#### Open-ended Feedback

```{r feedbackStudy3, fig.env="figure", fig.cap = "Children's Open-ended Feedback in Study 3. Error bars represent 95\\% confidence intervals." }

study3_feedback <-
  data_study3 %>%
  filter(feedback!="0") %>%
  group_by(id, Animal, Guess, feedback) %>%
  summarise(counts= n()) %>%
  spread(feedback, counts) %>%
  replace(is.na(.), 0) %>%
  mutate(total = J + D + C) %>%
  gather(feedback, counts, C:J) %>%
  mutate(prop = counts / total) %>%
  group_by(Animal, Guess, feedback) %>%
  summarize(cih = ci.high(prop),
            cil = ci.low(prop),
            prop = mean(prop))

study3_feedback$feedback <- 
  study3_feedback$feedback %>%
  factor() %>%
  fct_recode(Judgment = "J", Correction = "C", Description = "D") %>%
  fct_relevel(c("Judgment", "Description","Correction"))

study3_feedback$Guess <- 
  study3_feedback$Guess %>%
  factor() %>%
  fct_relevel("Z") %>%
  fct_recode(Cat = "X", Elephant = "Z", `Cat or Dog`="XorY", `Cat and Dog`="XandY")
  
study3_feedbackPlot <-
  ggplot(study3_feedback, 
       aes(x=feedback, y=prop, fill=feedback)) + 
  geom_bar(stat="identity", width = 0.6, position="dodge") + 
  geom_linerange(aes(ymax = cih, ymin = cil)) + 
  facet_grid(Animal~Guess) + 
  labs(title = "", x = "", y = "") + 
  theme_few() + 
  theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = .5), text= element_text(size=11, family= "Times")) + 
#  scale_fill_solarized(guide=FALSE)
  scale_fill_manual(values = c("red2", "red3", "red4"), guide=FALSE)

study3_feedbackPlot_g <- ggplot_gtable(ggplot_build(study3_feedbackPlot))

strips <- grep("strip-r", study3_feedbackPlot_g$layout$name)

new_grobs <- list(cat, cat_dog)

study3_feedbackPlot_g <- with(study3_feedbackPlot_g$layout[strips,],
          gtable_add_grob(study3_feedbackPlot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

study3_feedbackPlot_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(study3_feedbackPlot_g)
```

Figure \@ref(fig:feedbackStudy3) shows the distribution of children's feedback to the puppet in Study 3 (see Table \@ref(tab:feedbackCat) for the definitions and examples of feedback categories). There were no "None" responses in this study since the experimenter explicitly asked children to provide feedback to the puppet. The distribution of the responses in the other three categories (Judgment, Description, and Correction) revealed a successful replication of Study 2. 

Children's feedback showed four main patterns. First when the puppet guessed an animal not on the card (e.g. "There is an elephant!"), there is a split pattern between negative judgments like "No!" and simply mentioning the animal on the card (e.g. "Cat!"). Children provided no corrections on such trials, at least the way we have defined them. Second, almost all children responded with positive judgments like "Yes!" when the puppet's guess accurately matched what was on the card. This was the case in trials where there was only one animal on the card (e.g. cat) and the puppet mentioned it (e.g. "There is a cat!"), as well as trials where there were two animals on the card and the puppet mentioned both with a conjunction (e.g. "There is a cat and a dog!"). Third, children provided the largest number of corrective feedback in trials where the guess was either false or infelicitous. These included three trial types: (a) the ones where there were two animals on the card (e.g. cat and dog) but the puppet only guessed one (e.g. "There is a cat!"); (b) the ones where the puppet guessed two animals with conjunction (e.g. "There is a cat and a dog!") but only one of them was on the card (e.g. cat); and (c) the ones where there were two animals on the card (e.g. cat and dog), and the puppet guessed both but used a disjunction (e.g. "There is a cat or a dog!"). Finally, there was a pattern of feedback unique to disjunctive trials (e.g. "There is a cat or a dog!") with only one animal on the card (e.g. cat). In such cases, almost all children simply named the animal on the card (e.g. "Cat!").

```{r judgmentProptable}
judgment_data <- 
  data_study3 %>%
  filter(judgment!="YN") %>% # excluding the child that said yes and no.
  group_by(id, Animal, Guess, judgment) %>%
  summarise(counts= n()) %>%
  spread(judgment, counts) %>%
  replace(is.na(.), 0) %>%
  mutate(total = `0` + N + Y) %>%
  gather(judgment, counts, `0`:Y) %>%
  mutate(prop = counts / total) %>%
  group_by(Animal, Guess, judgment) %>%
  summarize(cih = ci.high(prop),
            cil = ci.low(prop),
            prop = mean(prop))

judgment_data$judgment <- fct_recode(judgment_data$judgment, No="N", `-`="0", Yes="Y")
judgment_data$judgment <- fct_relevel(judgment_data$judgment, "No", "-", "Yes")

judgment_data$Guess <- 
  judgment_data$Guess %>%
  factor(levels = c("Z", "X", "XandY", "XorY")) %>%
  fct_recode(Elephant = "Z", Cat = "X", `Cat and Dog`="XandY", `Cat or Dog`="XorY")
```

```{r study3JudgmentPlot, fig.env = "figure", fig.cap = "Children's open-ended feedback to the puppet's guesses. The x-axis shows whether children spontaneously provided a yes (green), no (red), or other response (grey)."}
judgment_plot <-
  judgment_data %>%
  ggplot(aes(x=judgment, y=prop, fill=judgment)) + 
  geom_bar(stat = "identity") + 
  geom_linerange(aes(ymax=cih,ymin=cil)) +
  facet_grid(Animal~Guess) + 
  theme_few() + 
  labs(x="", y="") +
  theme(text = element_text(size=11, family="Times")) +
  scale_fill_manual(values= c("red3", "grey", "springgreen3")) + guides(fill=FALSE)

judgment_plot_g <- ggplot_gtable(ggplot_build(judgment_plot))

strips <- grep("strip-r", judgment_plot_g$layout$name)

new_grobs <- list(cat, cat_dog)

judgment_plot_g <- with(judgment_plot_g$layout[strips,],
          gtable_add_grob(judgment_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

judgment_plot_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(judgment_plot_g)
```

Figure \@ref(fig:study3JudgmentPlot) breaks down children's open-ended feedback based on whether children said *Yes!*, *No!*, or said something else. Responses that were not yes/no judgments are grouped in a middle category shown with a dash. The goal here is to compare children's open-ended judgments with their forced choice judgments shown in Figure \@ref(fig:Study3tvjtPlot). Children's open-ended judgments and their forced choice judgments in study 3 show similar patterns for all types of guesses except for disjunctive ones. In trials that the puppet guessed a disjunction, the vast majority of children refused to provide a yes/no judgment when they were not forced to. Instead, they described the animal on the card or provided corrections to the puppet's infelicitous disjunctive guess.

One way to interpret these results is that disjunctive guesses (with at least one disjunct true) are considered neither right nor wrong. When children were forced to provide wrong/right responses in the experimental context, some conformed to the adult patterns of judgment and some did not. However, it is possible that such deviations from adult judgments do not reflect differences in the comprehension of disjunction, but rather differences in how children map their comprehension of disjunction onto the notions of "right" and "wrong" when forced to do so.

```{r feedbackFillData}
feedback_data <- 
  data_study3 %>%
  filter(feedback!="0")

feedback_data$Guess <- 
  feedback_data$Guess %>%
  factor() %>%
  fct_relevel("Z") %>%
  fct_recode(Cat = "X", Elephant = "Z", `Cat or Dog`="XorY", `Cat and Dog`="XandY")
feedback_data <- unite(feedback_data, Feedback, c(feedback, correction), sep="")

feedback_data$judgment <- fct_relevel(feedback_data$judgment, "N", "0", "Y", "YN")
feedback_data$judgment <- fct_recode(feedback_data$judgment, No="N", `-`="0", Yes="Y")

feedback_data$Feedback <- fct_relevel(feedback_data$Feedback, "J0", "D0", "CE" , "CI")
feedback_data$Feedback <- fct_recode(feedback_data$Feedback, `Yes/No` = "J0", `Just/Only Cat`="CE", `Both/Cat AND Dog`="CI", `Cat (and Dog)`="D0")
```
<!--
```{r feedbackFillPlot, fig.env="figure", fig.cap="Children's open-ended feedback. The x-axis shows whether children said yes or no and the color fill shows what children said other than yes/no."}
feedback_plot <-
  feedback_data %>%
  filter(judgment!="YN") %>%
  ggplot(aes(x=judgment, fill=Feedback, order=Feedback)) + geom_bar() + facet_grid(Animal~Guess) + theme_few() + labs(x="", y="") + scale_fill_manual(values= c("grey", "gold", "blue3", "red3")) + theme(text = element_text(size=10,family="Times"))

feedback_plot_g <- ggplot_gtable(ggplot_build(feedback_plot))

strips <- grep("strip-r", feedback_plot_g$layout$name)

new_grobs <- list(cat, cat_dog)

feedback_plot_g <- with(feedback_plot_g$layout[strips,],
          gtable_add_grob(feedback_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

feedback_plot_g$widths[[11]] <- unit(2.5,"cm")

grid.draw(feedback_plot_g)
```

Figure \@ref(fig:feedbackFillPlot) is similar to Figure \@ref(fig:study3JudgmentPlot) but it uses color-fill to show what children said in addition to "yes/no". The gray color represents the trials where children only said "yes/no" and nothing else. The yellow-fill represents descriptions where children mentioned the animal on the card (e.g. "cat!"). The blue fill represents children's corrective feedback that used the exclusive focus particles  *just* or *only* (e.g. "just a cat!"). Such a corrective feedback suggests that the guess included an animal that did not belong and should have been excluded. Finally the red fill represents the inclusive corrective feedback that emphasized the word *and* or said *both* (e.g. "Both!", "cat AND dog!"). Such corrective feedback indicated that both animals should have been mentioned.

As shown in the leftmost column, when the puppet mentioned an animal that was not on the card (e.g. elephant), children responded with a simple *No!* or *No!* followed by what was on the card (e.g. *No! Elephant!*). When there was only one animal on the card and the puppet mentioned the animal (e.g. *There is a cat!*), children responded with a simple *Yes!*. However, when the card had two animals (e.g. cat and dog) and the puppet only mentioned one of them (e.g. *there is a cat!*), children were likely to provide inclusive feedback. They said *both* or emphasized *and*, as in *cat AND dog!*. However, in such trials children were equally split between saying "yes", "no", or neither.

In the trials with conjunctive and disjunctive guesses, when there was only one animal on the card (e.g. cat) and the puppet used a conjunction (e.g. cat and dog), children were likely to say a simple *No!* or say *No!*, followed by "only/just" (e.g. no, just a cat). Some children did not say "no" but did respond with "only/just". When the card had two animals on it and the puppet mentioned both using *and*, children responded with a simple "yes". In trials with disjunctive guesses like "cat or dog", children avoided yes/no responses. Instead, when the card had only one animal, children mentioned that animal. When the card had both animals, children said *both* or emphasized the word *and*, as in "cat AND dog". 
-->
```{r inclusionTable}
inclusion_table <- 
  feedback_data %>%
  filter(judgment!="YN") %>%
  group_by(id, Animal, Guess, Feedback) %>%
  summarise(counts= n()) %>%
  spread(Feedback, counts) %>%
  replace(is.na(.), 0) %>%
  mutate(total = `Yes/No` + `Cat (and Dog)` + `Just/Only Cat` + `Both/Cat AND Dog`) %>%
  gather(Feedback, counts, `Yes/No`:`Both/Cat AND Dog`) %>%
  mutate(prop = counts / total) %>%
  group_by(Animal, Guess, Feedback) %>%
  summarize(cih = ci.high(prop),
            cil = ci.low(prop),
            prop = mean(prop))

inclusion_table$Feedback <- fct_relevel(inclusion_table$Feedback, "Yes/No", "Cat (and Dog)", "Just/Only Cat", "Both/Cat AND Dog")
```


```{r include=FALSE}
feedback_data %>%
  filter(Guess=="Cat or Dog", Animal=="X", Feedback=="Just/Only Cat", tvjt=="No")

feedback_data %>%
  filter(Guess=="Cat or Dog", Animal=="XY", id=="2017-06-07-14-3"|id=="2017-06-07-14-48")

feedback_data %>%
  filter(Guess=="Cat and Dog", Feedback=="Just/Only Cat", tvjt=="No")

```

```{r correctivePlot, fig.env="figure", fig.cap="Children's feedback categories in disjunction trials."}
inclusion_plot <-
  inclusion_table %>%
#  filter(Guess == "Cat or Dog") %>%
  ggplot(aes(x=Feedback, y=prop, fill=Feedback)) + geom_bar(stat="identity") +
  geom_linerange(aes(ymin=cil, ymax=cih)) + facet_grid(Animal~Guess) + labs(x="", y="") + theme_few() + scale_fill_manual(values=c("grey", "gold", "blue3" ,"red3")) + theme (text = element_text(size=11, family = "Times"), axis.text.x = element_text(angle=30, hjust = 1, vjust = 1)) + guides(fill=FALSE)

inclusion_plot_g <- ggplot_gtable(ggplot_build(inclusion_plot))

strips <- grep("strip-r", inclusion_plot_g$layout$name)

inclusion_plot_g <- with(inclusion_plot_g$layout[strips,],
          gtable_add_grob(inclusion_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        

inclusion_plot_g$widths[[12]] <- unit(2.5,"cm")

grid.draw(inclusion_plot_g)
```

Figure \@ref(fig:correctivePlot) shows the proportion of feedback categories other than yes/no judgments on the x-axis. Our goal here is to display the trial types with corrective feedback (blue and red). These trial types include: (1) conjunction when only one conjunct is true (e.g. guess: "There is a cat and a dog!", card: cat), (2) disjunction when both disjuncts are true (e.g. guess: "There is a cat or a dog", card: cat and dog), and (3) simple guesses when two animals were on the card (e.g. "There is a cat!", card: cat and dog). These trial types involved guesses that were either false or infelicitous. Furthermore, the type of corrective feedback children provided matched the type of mistakes made in the guesses. With conjunctive guesses (e.g. There is a cat and a dog!") when there was only one animal on the card (e.g. cat), children provided exclusive corrections (e.g. "Just/only a cat!"), suggesting that the other animal (e.g. dog) should have been excluded. When two animals were on the card (e.g. cat and dog) and the puppet used a disjunctive guess (e.g. "There is a cat or a dog!"), or simple guess (e.g. "There is a cat!"), children provided inclusive feedback, suggesting that another animal should have been included. This is particularly notable in the case of disjunction since both animals were mentioned, but children still emphasized that the connective *and* should have been used, or that *both* animals mentioned were on the card.

```{r eval=FALSE}
judg_agree <-
  data_study3 %>%
  select(Animal, Guess, tvjt, judgment)
  
judg_agree$tvjt <- as.character(judg_agree$tvjt)

judg_agree$tvjt[is.na(judg_agree$tvjt)] <- "0"

judg_agree$judgment <- 
  fct_recode(judg_agree$judgment,Yes="Y", No="N", `0`="YN")

agree_table <-
  judg_agree %>%
  group_by(Animal,Guess) %>%
  select(tvjt, judgment) %>%
  agree()

total_agree <-
judg_agree %>%
  select(judgment, tvjt) %>% 
  agree()

total_kappa <-
judg_agree %>%
  select(judgment, tvjt) %>% 
  kappa2()
```

### Discussion

Study 3 measured children's comprehension of logical connectives in two ways: First, with analyzing their open-ended feedback and second, with a two-alternative forced choice task. First, we asked children to say *yes* to the puppet if he was right and *no* if he was wrong. However, children could provide any form of feedback they wanted. Second, we followed children's open-ended feedback with a 2AFC question: "Was the puppet right?" This way, we could measure children's comprehension in two different ways in the same trial. Ideally, both measures should show similar results. However, the findings were similar for conjunctive guesses, but not disjunctive ones. Children avoided binary right/wrong feedback with disjunction and preferred to provide more nuanced feedback.

The 2AFC responses followed the predicted pattern: conjunctive guesses were judged wrong if only one conjunct was true, and right if both were true. Disjunctive guesses were judged right whether one or both disjuncts were true. There was no significant difference in the 2AFC task between the responses of children and those of adults in Study 1. Children's open-ended feedback in Study 3 replicated the findings of Study 2. Children provided more corrective feedback in false and infelicitous trials than in true and felicitous ones. The corrective feedback was tailored to the puppet's mistake. If the puppet used a conjunction when there was only one animal on the card, children pointed out that the other animal should have been excluded from the guess. They used the exclusive adverbials *just* and *only* in their feedback. If the puppet used a disjunction when both animals were on the card, children stressed *and* or *both*, implying that both animals should have been included. 

While the 2AFC results suggested that children took no issue with disjunctive guesses when both disjuncts were true, the analysis of their corrective feedback showed that they provide appropriate corrections in such cases and emphasized that the connective *and* would have been a better guess. Taking both measures together, we conclude that even though children are aware of the problem with such guesses, they do not consider them *wrong*.

## General Discussion {#discussion}

We reported three studies on adults' and preschool children's comprehension of the logical connectives *and* and *or*. The first study used two- and three-alternative forced choice judgment tasks with adults. In the 2AFC task, adult interpretations closely matched the semantic accounts of *and* and *or* as conjunction and inclusive disjunction. The 2AFC judgments did not register robust signs of pragmatic infelicities. However, the 3AFC judgments showed signs of pragmatic infelicities, especially in disjunctive guesses with true disjuncts. When two animals where on the card (e.g. cat and dog) and the guess used *or* (e.g. *There is a cat or a dog!*), participants were more likely to choose "kinda right" rather than "right".

The second study used a 3AFC judgment task with four-year-old children. It also included an exploratory analysis of children's open-ended verbal feedback to the puppet in the experimental setting. Children's interpretations were similar to those of adults in the 3AFC task and only differed for pragmatically infelicitous disjunctions. When both disjuncts were true, adults tended to judge disjunctive guesses as "kinda right". This was evidence for the pragmatic infelicity of such guesses. While, children judged such disjunctive statement as "right", the analysis of their open-ended feedback showed that they took issue with such statements as well, and provided appropriate corrective feedback.

In the third study, we focused on eliciting open-ended verbal feedback from children and followed it with a 2AFC question. Children's 2AFC responses reflected the semantics of the connectives *and* and *or* as conjunction and inclusive disjunction. There was no significant difference between children and adults in the 2AFC task.  Analysis of children's open-ended feedback replicated the findings in study 2. Children provided more corrective feedback in false and pragmatically infelicitous trials with the connectives than in felicitous trials. The comparison of the 2AFC task and children's open-ended responses showed that children are sensitive to the infelicity of disjunctions with true disjuncts, even though they consider them to be "right" guesses.

Previous studies had suggested that adults and preschool children differ in their interpretation of disjunction in two ways. First, unlike adults, children might interpret a disjunction as conjunction [@Singh2016; @tieu2016]. Second, children might interpret *or* as inclusive disjunction when adults interpret it as exclusive [@crain2012emergence]. The studies reported here provide evidence for the hypothesis that these differences may be an artifact of the experimental task and the type of measurement (@skordosEtal2018, @katsos2014scalar). 

Considering the first difference, in the 2AFC and 3AFC judgment tasks we found only small (but significant) preferences for both disjuncts being true rather than only one. Combining the 2AFC and the verbal feedback results, we expect that a child with strong conjunctive interpretation of disjunction should have rejected a disjunctive guess when only one disjunct was true, provided a "Just/Only" feedback, and accepted the guess when both disjuncts were true without providing a correction. We found no child in our sample that showed this pattern of responses. Two children who consistently rejected a disjunction when only one disjunct was true, provided corrective feedback when one or both disjuncts were true. Therefore while it is possible that some children interpret *or* as *and*, our results did not show a common or consistent effect.

We would like to add that conjunctive interpretations of disjunction, even when robustly observed, can have at least two potential explanations. First, non-linguistic interpretive strategies and preferences, due to task demands or unknown connective meaning [@paris1973comprehension; @clark1973non], and second, pragmatic enrichment, common in free-choice contexts [@Singh2016; @tieu2016]. As explained in section \@ref(litreview), previous research provides substantial evidence for task-related increase in conjunctive readings of disjunction [@neimarkSlotnick1970; @paris1973comprehension; @braine1981development; @skordosEtal2018]. In order to show instances of pragmatically enriched conjunctive readings in preschool children, it is important to first rule out task-related conjunctive interpretations.

Considering the second difference, namely the lower rate of exclusivity inferences in preschool children, our studies provided evidence that the choice of measurement may play an important role. In the 3AFC judgment task when two animals were on the card (e.g. card: cat and dog, guess: "There is a cat or a dog"), adults were more likely to choose "kinda right" than children were. Children mostly chose "right". However, in their free-form feedback, children corrected such utterances and suggested that the connective *and* should have been used instead of *or*. 

<!--The 3AFC respones can be taken to mean that children found no infelicity with such disjunctions or that they did not "derive an exclusivity implicature". This interpretation is consistent with the generalization that children are more likely than adults to interpret scalar terms literally, and that children do not compute implicatures or judge infelicity to the same "rate" that adults do [@pouscoulous2009going, @katsos2014scalar].-->There have been at least four major proposals to account for children's perceived low rate of "implicature computation": processing difficulty [@reinhart2004processing; @pouscoulous2007developmental], non-adult-like lexical entry [@barner2011accessing; @horowitz2017trouble], pragmatic tolerance [@katsos2011pragmatic], and the role of experimental measurement [@katsos2014scalar]. Below we argue that the first three cannot explain the reported results of children's forced judgments and free-form feedback, and that these results highlight the role of experimental measurement as a source of perceived differences in children and adults pragmatic inferences.

**1. Processing difficulty.** First, processing accounts locate the problem in children's processing capacities such as working memory. They suggest that pragmatic computations are cognitively taxing and children lack the appropriate processing resources to carry them out appropriately. A prediction of processing accounts (at least in their current format) is that children will show reduced implicature computations for all types of implicatures -- scalar or not. This prediction was not borne out in our experimental results here. In Study 3, children were much more likely than adults to call a simple guess (e.g. *There is a cat!*) "wrong" if there were two animals on the card (e.g. cat and dog). In other words, children's interpretations were much more exhaustive than adults. Processing accounts do not predict that children may derive implicatures at a higher rate than adults but this is what we found, at least for the traditional interpretation of the judgment task.

**2. Non-adult-like Lexicon.** Several proposals blame the structure of the child's lexicon for the alleged failure in deriving implicatures. The assumption is that the child's lexical entry for scalar items must include three elements for successful derivation: 1. the semantics of the weak term (e.g. *some*, *or*) 2. the semantics of the strong term (e.g. *all*,*and*); and possibly 3. a scale that recognizes the stronger term as an alternative to the weaker one (e.g. <*some*, *all*>, <*or*, *and*>). Each of these elements have been pinpointed as the source of the problem in previous studies [@horowitz2017trouble; @katsos2011pragmatic; @barner2011accessing]. However none of them seem to apply to the results reported here.

If children in this study lack the semantics of the connective *or*, we would expect them to either perform at chance or default to a conjunctive interpretation. Neither prediction was borne out in studies 2 and 3. Furthermore, children's free-form linguistic feedback in both studies suggested that children understood disjunction  well enough to provide relevant feedback. So this explanation seems unlikely. The problem cannot be that children do not know the meaning of *and* either. Children's performance in both study 2 and 3 for conjunction trials show that they understand its meaning very well. Finally, comparing children's truth value judgments and their free-form verbal feedback, we found that many children judged a disjunction with true disjuncts as "right", yet went on to correct the puppet and explicitly mention *and* as the connective he should have used. If children could not access the stronger alternative, they could not have mentioned it in their feedback either. And if accessing the stronger alternative would have resulted in expressing sub-optimal judgments, they should not have judged the guess as "right".

**3. Pragmatic Tolerance.** Katsos \& Bishop [-@katsos2011pragmatic] suggested that children tend to tolerate pragmatic infelicities more than adults. They showed that when children were provided with a 2AFC judgment task, they considered a description with the scalar term *some* as "right" when *all* was more informative (e.g. *The turtle played with some of the balls.*, Scene: the turtle played with all the balls.) However, when they are presented with three options (small, big, and huge strawberries) in a 3AFC task, they choose the middle option in the same type of trials. They argued that children tolerate pragmatic infelicities and do not regard them as "wrong". As in a processing account, the tolerance account predicts that scalar and ad-hoc implicatures will be similarly affected. However, our results did not match those of Katsos \& Bishop [-@katsos2011pragmatic]. When children were presented with a 3AFC task, they chose the highest reward (and not the middle option) for uses of *or* when *and* was more informative. Second, and more importantly, we found different patterns for exhaustive and scalar inferences as mentioned before. This is not predicted by the tolerance account unless we assume that children are more tolerant towards violations of scalar inferences than they are towards exhaustive ones. While this is not currently assumed in the literature, it is a possible adjustment. However, we would like address this issue by focusing on another related factor: the role of measurement in estimates of children's pragmatic capacity [@katsos2014scalar]. 

**4. The Role of Measurment.** Two observations in the current studies provide support for the hypothesis that methodological issues, and more specifically issues of measurement contribute to the differences found between adults and children in pragmatic capacity. First, Study 1 showed that even for adults, the estimates of adult infelicity rates may differ based on the number of alternatives in the forced choice task. A 2AFC task underestimated adults' sensitivity to pragmatic infelicity. In fact, in a follow up study, we systematically varied the number of response options and replicated the results presented here (see Jasbi, Waldon, and Degen in press). Second, children's open-ended linguistic feedback in the experimental context better reflected their sensitivity to pragmatic nuances than the forced-choice judgment tasks. Third, children showed a higher rate of "wrong" judgments for cases of exhaustive inferences (simple guesses with two animals on the card) than adults did. While a difference in sensitivity to ad-hoc vs. scalar implicatures has been reported and argued for before [@stiller2015ad; @horowitz2017trouble], a higher sensitivity than adults is not predicted by any of the current accounts. 

```{r implicatureGraph, fig.env = "figure", fig.cap = "Factors that could affect pragmatic computations and the estimates of these computations in the experimental settings"}
implicature_img <- jpeg::readJPEG("figs/implicature.jpg")
grid::grid.raster(implicature_img)
```

Figure \@ref(fig:implicatureGraph) shows a summary of the factors that are proposed to affect pragmatic computations. As Pouscoulous \& Noveck [-@pouscoulous2009going] and Katsos [-@katsos2014scalar] have suggested, the central issue is "the rate" at which children and adults manifest pragmatic reasoning in the experimental setting. No one doubts children's capacity to perform such computations. At issue is the extent to which children and adults compute specific implicatures. As Katsos [-@katsos2014scalar] pointed out, it seems reasonable to assume that all these factors play some part here. What matters is the degree to which each contributes to the outcome. 

The results of the studies reported here suggest that it is important to distinguish between factors that affect pragmatic computations and those that affect the observed "rate" in an experimental setting. As we showed in Study 1, given the number of alternatives in the forced choice task (2AFC vs. 3AFC), we may get different estimates of adults' rate of infelicity judgments, but we cannot assume that there is a difference in adults' pragmatic capacities in these two tasks. A similar situation exists when we compare children's forced choice measures of infelicity and their open-ended feedback.

In order to better understand the differences between adults and children's semantic and pragmatic capacities, it is necessary to have a good understanding of how our measurements affect estimates of adults and children's performance in the experimental tasks. Children may be no more capable of making exhaustive inferences than adults and no less capable of making scalar inferences either. They may simply have a different construal of the wrong-right scale and of what the forced-choice task is about. The concepts "right" and "wrong" are as much subject to developmental change and differences between adults and children as are scalar items that constitute the focus of our studies. Relying on a single type of measurement increases the risk of measurement-specific conclusions. Using multiple measurements in the same task can provide converging evidence for felicity/infelicity or presence/absence of specific inferences. Ultimately, in order to capture semantic and pragmatic competences of adults and (especially) children, we need to develop methods that can reliably tap into specific dimensions of meaning.

<!--
It is possible that children's understanding of what constitutes as "right" or "wrong" does not fully conform to that of adults. However, it remains to be established what these differences are and how they affect the estimates of children's pragmatic abilities. 
-->
## Conclusion{#conclusion}

We provided three studies that tested adults and children's comprehension of disjunction in existential sentences using three different measures: binary forced-choice truth value judgments (2AFC task), ternary forced-choice truth value judgments (3AFC task), and free-form verbal feedback. The results suggested that for each population, different measures were sensitive to different aspects of meaning. The binary measure captured children and adults intutions about truth values well: it showed that they considered a disjunction as inclusive in existential sentences of the guessing game. Ternary judgments provided evidence for adults' pragmatic inferences: adults often considered a disjunction when both disjuncts were true as "kinda right" and not completely right. For children, the ternary judgments did not register such an effect, but their free-form verbal feedback did. When both disjuncts were true, children verbally corrected the puppet and suggested that he should have said *and* instead of *or*. The combination of children's truth valued judgments and their verbal feedback suggested that on average, children in our sample understood that when both propositions were true, their conjunction and disjunction were true, yet conjunction made a more appropriate and felicitous utterance.

Since Tarski's original observations on disjunction, research in semantics and pragmatics has shown that the variety of interpretations Tarski observed are in fact distinct types of meaning observed in many aspected of langauge and connected to distinct processes that generate them. Therefore, while the inclusive interpretation is hypothesized to be part of *or*'s semantics, exclusivity and ignorance interpretations are analyzed as distinct pragmatic inferences generated separately. This theoretical insight has in turn lead developmental researchers to seek distinct developmental mechanisms for each type of meaning. The results of the studies reported here suggest that as more and more varieties of meaning become subject of experimental study, we also need to develop measures especially suited to capture the aspect of meaning under investigation.

\newpage

# References

```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}